---
title: "Analyses"
description: "This document entails the model-based analyses ('4_modeling.R), visualises the data, tests assumptions, and examines the confirmatory and exploratory results."
author:
  - name: Lukas Gunschera
    orcid: 0000-0002-8241-0833
    email: l.gunschera@outlook.com
    corresponding: true
    affiliation:
      - ref: 1
affiliations:
  - id: 1
    name: University of Cambridge
    department: Medical Research Council Cognition and Brain Sciences Unit
format:
  html:
    code-fold: true
    toc: true
editor: visual
---

```{r}
#| label: setup-document
#| include: false
#| message: false
#| cache: false

# set parameters and seed
source(here::here("code", "00_setup.R"))
set.seed(777)

# configure global output options for the document
is_html <- knitr::is_html_output()
knitr::opts_chunk$set(
  eval = TRUE,
  cache = FALSE,  # disable global caching by default
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  echo = is_html,
  fig.width = 7,
  fig.height = 5,
  dpi = 800,
  dev = "ragg_png"  # use ragg_png for better rendering performance
)

# load dependencies
pacman::p_load(gt, zoo, plm, glue, brms, ragg, here, nlme, knitr, purrr, dplyr, tidyr, knitr, Hmisc, effsize, viridis, stringr, rstatix, janitor, ggplot2, ggExtra, devtools, gtExtras, magrittr, hBayesDM, corrplot, extrafont, patchwork, ggpattern, bayesplot, tidybayes, lubridate, posterior, tidyverse, BayesFactor, systemfonts, cowplot)

# load custom helper and plotting functions
source(here::here("code", "experiment2", "functions", "fun_plots.R"))
source(here::here("code", "experiment2", "functions", "fun_helper.R"))
```

```{r}
cat("Document rendered at:", format(Sys.time(), "%Y-%m-%d %H:%M:%S"))
```

## Data

Load processed participant data as returned from the script 'code/4_modeling' and based on dependencies '1_parsing.R', '2_descriptive.R', and '4_modeling.R'. Scripts are split to reduce computational demands.

You can run the below chunk to fit the models (set run_models to TRUE) - but we suggest running this file independently.

```{r}
#| label: fit-models-file
#| message: false
#| warning: false
#| cache: false

#run_models <- FALSE  # set to TRUE to run the models (note: this will take a long time)
#source(here::here("code", "experiment2", "03_modelling.R"))
```

```{r}
#| label: data-import

# load individual-level model parameters from the winning model (m3)
data_params <- readRDS(here::here("data", "experiment2", "modelling", "parameters", "m3_para_data.RDS"))

# load the full cleaned dataset including trial-level choice data
data <- readRDS(here::here("data", "experiment2", "processed", "data_clean.RDS"))
```

## Descriptive Statistics

First, we have a closer look at the demographic data of participants to characterise the sample.

```{r}
#| label: descriptive-stats-table
#| echo: true
#| warning: false
#| message: false
#| output: asis

data_params |>
  dplyr::select(age, gender, ethnicity, income_value, income_currency, 
                neuro_screening, mh_screening) |>
  dplyr::mutate(income_gbp = case_when(
    income_currency == "usd" ~ income_value * 0.73243115, # convert usd income to gbp using approximate exchange rate
    TRUE ~ income_value
  )) |>
  dplyr::summarise(
    n = n(),
    mean_age = mean(age),
    sd_age = sd(age),
    min_age = min(age),
    max_age = max(age),
    median_income = median(income_gbp),
    sd_income = sd(income_gbp),
    mean_income = mean(income_gbp)
  ) |>
  dplyr::mutate(across(where(is.numeric), ~sprintf("%.3f", .))) |>
  knitr::kable(
    caption = "Descriptive Statistics",
    col.names = c("N", "Mean Age", "SD Age", "Min Age", "Max Age", 
                  "Median Income (GBP)", "SD Income", "Mean Income (GBP)")
  )
```

Following an overview of the quantitative descriptives above, let's have a closer look at the qualitative demographics including ethnicity and mental health conditions.

```{r}
#| label: categorical-stats-labeled
#| echo: true
#| warning: false
#| message: false

# pivot categorical variables to long format to compute frequencies and percentages per category
data_params |>
  dplyr::select(gender, ethnicity, neuro_screening, mh_screening) |>
  dplyr::mutate(across(everything(), as.character)) |>
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "category"
  ) |>
  dplyr::group_by(variable, category) |>
  dplyr::summarise(
    n = n(),
    .groups = "drop"
  ) |>
  dplyr::group_by(variable) |>
  dplyr::mutate(
    percent = sprintf("%.3f%%", (n / sum(n)) * 100)
  ) |>
  dplyr::arrange(variable, desc(n)) |>
  knitr::kable(
    caption = "Categorical Variable Frequencies",
    col.names = c("Variable", "Category", "N", "Percentage")
  )
```

Here's an overview of the mental health conditions in the sample.

```{r}
#| label: mental-health-prevalence-html
#| echo: true
#| warning: false
#| message: false
#| output: asis

# count participants with each diagnosis using dedicated columns and free-text screening fields
mh_overview <- data_params |>
  dplyr::summarise(
    `Depression` = sum(mh_mdd | grepl("depression", mh_other, ignore.case = TRUE), na.rm = TRUE),
    `Bipolar Disorder` = sum(mh_bpd, na.rm = TRUE),
    `Anxiety disorder` = sum(mh_gad | grepl("anxiety", mh_other, ignore.case = TRUE), na.rm = TRUE),
    `Obsessive-Compulsive Disorder` = sum(mh_ocd, na.rm = TRUE),
    `Autism Spectrum Disorder` = sum(mh_autism, na.rm = TRUE),
    `Attention-Deficit Hyperactivity Disorder` = sum(grepl("adhd|add", mh_other, ignore.case = TRUE), na.rm = TRUE),
    `Borderline Personality Disorder` = sum(grepl("\\bBPD\\b", mh_other), na.rm = TRUE),
    `Post-Traumatic Stress Disorder` = sum(grepl("ptsd", mh_other, ignore.case = TRUE), na.rm = TRUE)
  ) |>
  tidyr::pivot_longer(everything(), names_to = "Diagnosis", values_to = "n") |>
  # express each count as a percentage of the full sample and of the mh-screened subsample
  dplyr::mutate(
    `% of sample` = sprintf("%.3f%%", (n / nrow(data_params)) * 100),
    `% of mental health` = sprintf("%.3f%%", (n / sum(data_params$mh_screening, na.rm = TRUE)) * 100)
  )

# display formatted table
knitr::kable(mh_overview, 
             caption = "Mental Health Diagnoses Overview",
             align = c("l", "r", "r", "r"))
```

Participants complete the effort-based decision-making task in both condition (devaluation, baseline). The below table illustrates the time from start of the task until end. This time excludes the instructions and calibration.

```{r}
#| label: task-duration
#| echo: true
#| warning: false
#| message: false
#| output: asis

# compute per-session duration for each participant, excluding the calibration phase
duration_results <- data$game_meta |>
  dplyr::filter(task_condition != "calibration") |>
  dplyr::group_by(subj_id, task_condition) |>
  dplyr::summarise(
    session_duration = sum(as.numeric(end_time - start_time)), 
    .groups = "drop"
  ) |>
  dplyr::arrange(subj_id, task_condition) |>
  dplyr::group_by(subj_id) |>
  dplyr::filter(n() >= 2) |>
  dplyr::mutate(session_order = row_number()) |>
  dplyr::ungroup() |>
  # summarise duration statistics overall and separately by session order (baseline = 1, devalued = 2)
  dplyr::summarise(
    mean_duration = mean(session_duration),
    sd_duration = sd(session_duration),
    min_duration = min(session_duration),
    max_duration = max(session_duration),
    mean_duration_baseline = mean(session_duration[session_order == 1]),
    mean_duration_devalued = mean(session_duration[session_order == 2]),
    sd_duration_baseline = sd(session_duration[session_order == 1]),
    sd_duration_devalued = sd(session_duration[session_order == 2])
  ) |>
  dplyr::mutate(across(where(is.numeric), ~sprintf("%.3f", .)))

duration_results |>
  knitr::kable(
    caption = "Session Duration Statistics (seconds)",
    col.names = c(
      "Mean", "SD", "Min", "Max",
      "Mean Baseline", "Mean Devalued", "SD Baseline", "SD Devalued"
    )
  )
```

```{r}
#| label: task-accepted-sucess-rate

# rate of accepted challenges
data$game |> 
  dplyr::filter(phase == "game") |> 
  # accepted trials
  dplyr::filter(choice == 1) |> 
  group_by(subj_id) |> 
  reframe(prop_accept = n() / 64) |> 
  reframe(mean_prop_accept = mean(prop_accept)*100, 
          sd_prop_accept = sd(prop_accept)*100, 
          min_prop_accept = min(prop_accept), 
          max_prop_accept = max(prop_accept))

# successrate of accepted challenges
p_succ <- data$game |> 
  dplyr::filter(phase == "game") |> 
  # accepted trials
  dplyr::filter(choice == 1) |> 
  dplyr::group_by(subj_id) |> 
  reframe(prop_success = sum((goalClicks - clicks) <= 0) / n()) |> 
  reframe(mean_prop_sucess = mean(prop_success)*100, 
          sd_prop_sucess = sd(prop_success)*100)
```

The modeling procedure utilises all trials without regard for the fact whether participants accept trials that they end up failing. A look at the data reveals that participants fail close to no offers that they accept: `r sprintf("%.3f", p_succ[1])`

Examine trial behaviour on a condition basis.

```{r}
#| label: acceptance-bayestest

# calculate acceptance proportions per participant
acceptance_props <- data$game |> 
  dplyr::filter(phase == "game") |> 
  dplyr::filter(task_condition %in% c("baseline", "devalued")) |>
  dplyr::filter(choice == 1) |> 
  dplyr::group_by(subj_id, task_condition) |> 
  dplyr::summarise(
    prop_accept = n() / 32,  # 32 trials per condition
    .groups = "drop"
  ) |>
  tidyr::pivot_wider(
    names_from = task_condition,
    values_from = prop_accept,
    values_fill = 0 # put zero for participants accepting no trials (all participants accepted some across entire study)
  )

# calculate means for reporting
baseline_mean <- mean(acceptance_props$baseline, na.rm = TRUE) * 100
devalued_mean <- mean(acceptance_props$devalued, na.rm = TRUE) * 100

# Bayesian paired t-test
bf_result <- ttestBF(
  x = acceptance_props$baseline,
  y = acceptance_props$devalued,
  paired = TRUE,
  rscale = "medium"  # Cauchy prior width (medium = sqrt(2)/2 ≈ 0.707)
)

# extract results
bf_value <- extractBF(bf_result)[1, "bf"]
bf_value

# extract the posterior samples
posterior_samples <- BayesFactor::posterior(bf_result, iterations = 10000)

# get median effect size
median_effect <- median(posterior_samples[, "delta"])

# get 95% credible interval
credible_interval <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))
```

The ***BF10*** **of `r round(bf_value, 3)`** indicates strong support for the null hypothesis that acceptance rates did not differ between the baseline and devalued conditions within subjects. The median standardised effect size was `r sprintf("%.3f", median_effect)`, and the *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval[1])` to `r sprintf("%.3f", credible_interval[2])`.

```{r}
#| label: acceptance-bayestest-groups

# calculate overall acceptance proportions for each subject (collapsing across conditions)
acceptance_overall <- data$game |> 
  dplyr::filter(phase == "game") |> 
  dplyr::filter(task_condition %in% c("baseline", "devalued")) |>
  dplyr::group_by(subj_id, group) |> 
  dplyr::summarise(
    prop_accept = sum(choice == 1, na.rm = TRUE) / 64,  # 64 total trials (32+32)
    .groups = "drop"
  )

# extract data for each group
addiction_props <- acceptance_overall |> 
  dplyr::filter(group == "addiction") |> 
  dplyr::pull(prop_accept)

control_props <- acceptance_overall |> 
  dplyr::filter(group == "control") |> 
  dplyr::pull(prop_accept)

# means for reporting
addiction_mean <- mean(addiction_props) * 100
control_mean <- mean(control_props) * 100


bf_result <- ttestBF(
  x = addiction_props,
  y = control_props,
  paired = FALSE,
  rscale = "medium"
)

# Extract results
bf_value <- extractBF(bf_result)[1, "bf"]
bf_value

# extract the posterior samples
posterior_samples <- BayesFactor::posterior(bf_result, iterations = 10000)

# get 95% credible interval
credible_interval <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))
```

Participants behaviour on the task is presented below.

```{r}
#| label: plot-task-descriptives

# accepted challenges plot
acceptance_plot <- task_plot(data$game, 
                             main_title = "", 
                             plot_type = "line_plot",
                             arrange_cols = 0, arrange_rows = 0) +
  labs(x = "Effort level", y = "Acceptance probability (SE)") +
  theme_custom()

acceptance_plot

# save rds
saveRDS(acceptance_plot, here::here("output", "rds", "gg_taskbehaviour_exp2.rds"))

# save ggplot
ggsave(
  acceptance_plot,
  filename = here::here("output", "figures", "experiment2", "task_behaviour.png"),
  width = 7,
  height = 5,
  dpi = 800,
  background = "white"
)
```

# Matching

We matched the addiction and no-addiction groups on age and gender. To confirm this, we perform the relevant statistical tests below.

```{r}

# bayesian independent-samples t-test for age
tbf_age <- BayesFactor::ttestBF(
  formula = age ~ group,   
  data = data_params,
  rscale = 1/3       
)

print(tbf_age)

# build a 2x2 contingency table of group by gender for the chi-square analogue
gender_table <- table(data_params$group, data_params$gender)

# totals (row margins) are fixed by design, which matches the matched-sample setup
tbf_gender <- BayesFactor::contingencyTableBF(
  gender_table,
  sampleType = "indepMulti",
  fixedMargin = "rows"        
)

print(tbf_gender)
```

The results indicate that the matching procedure was successful, and the groups do not differ on age or gender.

# Task Validation

First, let's validate the effort-expenditure task. To this end, we reproduce the expected effort discounting effects using a mixed-effects analysis of variance on the mean proportion of trials accepted per participant, as a function of effort and reward levels.

```{r}
#| label: task-validation-anova
#| echo: false
#| warning: false
#| message: false
#| output: asis

# aggregate to mean acceptance rate per participant, effort level, and reward level
choice_data <- data$modelling_data |> 
  dplyr::group_by(subjID, effort_a, amount_a) |> 
  dplyr::summarize(mean_choice = mean(choice))

# fit a linear mixed-effects model with random intercepts per subject and a full factorial design 
anov_ebdm <- anova(nlme::lme(mean_choice ~ effort_a * amount_a, random= ~1|subjID, data = choice_data))
```

The ANOVA revealed significant main effects of effort (*F*(1, `r anov_ebdm$denDF[2]`) = `r round(anov_ebdm[2, "F-value"], 3)`, *p* \< .0001) and reward (*F*(1, `r anov_ebdm$denDF[3]`) = `r round(anov_ebdm[3, "F-value"], 3)`, *p* \< .0001), as well as a significant interaction (*F*(1, `r anov_ebdm$denDF[4]`) = `r round(anov_ebdm[4, "F-value"], 3)`, *p* \< .0001).

Below we perform post-hoc ANOVAs for the individual effort and reward levels.

```{r}
#| label: task-validation-posthoc
#| echo: false
#| warning: false

# extract sorted unique levels of effort and reward for indexing in the post-hoc tests
effort_levels <- choice_data$effort_a |> unique() |> sort()
amount_levels <- choice_data$amount_a |> unique() |> sort()

# post-hoc anova: effect of effort at each reward level separately
anov_effort_1 <- anova(lme(mean_choice ~ effort_a, random= ~1|subjID, data = choice_data |> 
            dplyr::filter(amount_a == amount_levels[1])))
anov_effort_2 <- anova(lme(mean_choice ~ effort_a, random= ~1|subjID, data = choice_data |> 
            dplyr::filter(amount_a == amount_levels[2])))
anov_effort_3 <- anova(lme(mean_choice ~ effort_a, random= ~1|subjID, data = choice_data |> 
            dplyr::filter(amount_a == amount_levels[3])))
anov_effort_4 <- anova(lme(mean_choice ~ effort_a, random= ~1|subjID, data = choice_data |> 
            dplyr::filter(amount_a == amount_levels[4])))

# post-hoc anova: effect of reward at each effort level separately
anov_reward_1 <- anova(lme(mean_choice ~ amount_a, random = ~1|subjID, data = choice_data |> 
            dplyr::filter(effort_a == effort_levels[1])))
anov_reward_2 <- anova(lme(mean_choice ~ amount_a, random = ~1|subjID, data = choice_data |> 
            dplyr::filter(effort_a == effort_levels[2])))
anov_reward_3 <- anova(lme(mean_choice ~ amount_a, random = ~1|subjID, data = choice_data |> 
            dplyr::filter(effort_a == effort_levels[3])))
anov_reward_4 <- anova(lme(mean_choice ~ amount_a, random = ~1|subjID, data = choice_data |> 
            dplyr::filter(effort_a == effort_levels[4])))
```

Post-hoc analyses confirmed that effort significantly reduced acceptance rates at each reward level (all *p*s \< .0001): reward level 1 (*F*(1, `r anov_effort_1$denDF[2]`) = `r round(anov_effort_1[2, "F-value"], 3)`), reward level 2 (*F*(1, `r anov_effort_2$denDF[2]`) = `r round(anov_effort_2[2, "F-value"], 3)`), reward level 3 (*F*(1, `r anov_effort_3$denDF[2]`) = `r round(anov_effort_3[2, "F-value"], 3)`), and reward level 4 (*F*(1, `r anov_effort_4$denDF[2]`) = `r round(anov_effort_4[2, "F-value"], 3)`). Similarly, reward amount significantly increased acceptance rates at each effort level (all *p*s \< .0001): effort level 1 (*F*(1, `r anov_reward_1$denDF[2]`) = `r round(anov_reward_1[2, "F-value"], 3)`), effort level 2 (*F*(1, `r anov_reward_2$denDF[2]`) = `r round(anov_reward_2[2, "F-value"], 3)`), effort level 3 (*F*(1, `r anov_reward_3$denDF[2]`) = `r round(anov_reward_3[2, "F-value"], 3)`), and effort level 4 (*F*(1, `r anov_reward_4$denDF[2]`) = `r round(anov_reward_4[2, "F-value"], 3)`).

```{r}
#| label: fig-acceptance-line
#| fig-cap: "Acceptance proportion across effort levels for different reward levels (line plot)"
#| fig-width: 6
#| fig-height: 4

# line plot showing the continuous effort discounting effect across reward levels
acceptance_line <- task_plot(
  data$modelling_data, 
  main_title = "", 
  plot_type = "line_plot",
  arrange_cols = 0, 
  arrange_rows = 0
) + theme_custom() +
  labs(x = "Effort level", y = "Acceptance probability (SE)") 

print(acceptance_line)
```

```{r}
#| label: fig-acceptance-bar
#| fig-cap: "Acceptance proportion by effort level for each reward level (bar plots)"
#| fig-width: 8
#| fig-height: 6

# bar plots arranged in a 2x2 grid, one panel per reward level
acceptance_bar <- task_plot(
  data$modelling_data, 
  main_title = "", 
  plot_type = "bar_plot",
  arrange_cols = 2, 
  arrange_rows = 2
)

print(acceptance_bar)

saveRDS(acceptance_bar, here::here("output", "rds", "gg_taskbehaviour_exp2_bar.rds"))

ggsave(
  acceptance_bar,
  filename = here::here("output", "figures", "experiment2", "task_behaviour_bar.png"),
  width = 8,
  height = 6,
  dpi = 800,
  background = "white"
)
```

@fig-acceptance-line illustrates that participants were less likely to accept offers with increasing effort. The bar plots in @fig-acceptance-bar further show that acceptance rates were the highest for higher reward levels, and how acceptance decreased within each reward level as a function of increasing effort.

# Manipulation Check

Critical for the present experiment was the devaluation manipulation. We observed large effect sizes on self-reported liking in a pilot study for the combination of no colour and no sound in particular. In the below, we examine whether this manipulation was also effective in the test dataset examining self-reported levels of liking between the two conditions (baseline/devalued).

```{r}
#| label: manipulation-check

# compute descriptive statistics for self-reported liking in each condition
mean(data_params$liking_b)
sd(data_params$liking_b)
mean(data_params$liking_d)
sd(data_params$liking_d)

# bayesian paired t-test comparing liking between baseline and devaluation conditions
tbf_att <- BayesFactor::ttestBF(
  x = data_params$liking_b,
  y = data_params$liking_d,
  paired = TRUE,
  rscale = 1/3
)

# extract the bayes factor (bf10: evidence for h1 over h0)
bf10_att <- extractBF(tbf_att)$bf

# draw mcmc posterior samples to characterise the posterior distribution
posterior_samples_att <- posterior(tbf_att, iterations = 10000)

# extract the standardised effect size (delta) from posterior samples
delta_samples_att <- posterior_samples_att[, "delta"]

# compute the 95% credible interval for delta
credible_interval_att <- quantile(posterior_samples_att[, "delta"], probs = c(0.025, 0.975))

# summarise the posterior distribution of the effect size
delta_mean <- mean(delta_samples_att)
delta_median <- median(delta_samples_att)
delta_sd <- sd(delta_samples_att)
delta_ci <- quantile(delta_samples_att, probs = c(0.025, 0.975))
```

The ***BF10*** **of `r round(bf10_att, 3)`** indicates extreme support for the alternative hypothesis that *liking* is different between the baseline and the devaluation conndition within subjects. The *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval_att[1])` to `r sprintf("%.3f", credible_interval_att[2])`.

*Delta (δ)* for difference in self-reported liking between the baseline and devalued condition is **`r sprintf("%.3f", delta_mean)`** with a 95% Credible Interval ranging from `r sprintf("%.3f", delta_ci[1])` to `r sprintf("%.3f", delta_ci[2])`.

```{r}
#| label: fig-manipulation-check
#| fig-cap: "Liking difference between baseline and devaluation condition."
#| fig-width: 8
#| fig-height: 6

# pre-compute condition medians for the median indicator points on the plot
medians <- data_params |>
  tidyr::pivot_longer(cols = c(liking_b, liking_d),
               names_to = "condition",
               values_to = "liking") |>
  group_by(condition) |>
  dplyr::summarise(median_val = median(liking, na.rm = TRUE))

# density plot overlaid with credible interval bands and median points
ggplot_liking_dens <- data_params |>
  tidyr::pivot_longer(cols = c(liking_b, liking_d),
               names_to = "condition",
               values_to = "liking") |>
  ggplot2::ggplot(aes(x = liking, fill = condition, group = condition)) +
  ggplot2::geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  # add interval bands below the density curve (66%, 95% credible intervals)
  ggdist::stat_interval(
    aes(y = -0.02, colour = condition),
    position = position_dodge(width = 0.035),
    orientation = "horizontal",
    linewidth = 3,
    alpha = 0.3,
    show.legend = FALSE
  ) +
  # overlay median points using pre-calculated values to avoid position jitter
  geom_point(
    data = medians,
    aes(x = median_val, y = -0.02, fill = condition, colour = condition),
    size = 2,
    shape = 19,
    alpha = 1,
    stroke = 1,
    position = position_dodge(width = 0.035, orientation = "y"),
    inherit.aes = FALSE,
    show.legend = FALSE
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("liking_b" = "Baseline", "liking_d" = "Devalued")) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("liking_b" = "Baseline", "liking_d" = "Devalued")) +
  labs(x = "Self-reported liking", y = "Density", fill = "Condition") +
  scale_x_continuous(limits = c(0, 7), breaks = seq(0,7,1)) +
  scale_y_continuous(limits = c(-0.03, NA), breaks = seq(0, 0.5, 0.1)) +
  theme_custom() +
  theme(legend.title = element_blank(),
        legend.position = c(0.1, 0.9),
        legend.background = element_blank(),
        legend.key = element_blank()) 

# return plot
print(ggplot_liking_dens)

saveRDS(ggplot_liking_dens, here::here("output", "rds", "gg_liking_exp2.rds"))

# save high-resolution figure to the output directory
ggplot2::ggsave(
  filename = here::here("output", "figures", "experiment2", "fig-liking-manipulation.png"),
  plot = ggplot_liking_dens,
  width = 8,
  height = 6,
  dpi = 600
)
```

@fig-manipulation-check illustrates the distribution of self-reported liking in the baseline and devaluation conditions. The devaluation manipulation was successful, with participants reporting substantially lower liking in the devaluation condition compared to the baseline condition.

# Main Analyses

## Hypothesis 1

*Hypothesis 1:* *Wanting* (acceptance bias parameter) is higher for Baseline than for Devaluation condition.

Below, I perform a Bayesian paired samples t-test on the choice bias parameter (a), testing for differences between the baseline and devaluation condition within all subjects.

```{r}
#| label: hypothesis1-test
#| tbl-cap: "Bayesian paired t-test for wanting (a parameter) between baseline and devaluation conditions"
#| cache: false

# bayesian paired t-test: within-subject comparison of the acceptance bias (α) between baseline and devaluation conditions
tbf_h1 <- BayesFactor::ttestBF(
  x = data_params$a_baseline,
  y = data_params$a_devalued,
  paired = TRUE,
  rscale = 1/3
)

# extract the bayes factor (bf10)
bf10_h1 <- extractBF(tbf_h1)$bf

# draw mcmc samples from the posterior to characterise uncertainty
posterior_samples_h1 <- BayesFactor::posterior(tbf_h1, iterations = 10000)

# isolate the standardised effect size (delta) column from the posterior matrix
delta_samples_h1 <- posterior_samples_h1[, "delta"]

# 95% credible interval on the effect size
credible_interval_h1 <- stats::quantile(posterior_samples_h1[, "delta"], probs = c(0.025, 0.975))

# compute summary statistics for inline reporting
delta_mean <- mean(delta_samples_h1)
delta_median <- median(delta_samples_h1)
delta_sd <- sd(delta_samples_h1)
delta_ci <- quantile(delta_samples_h1, probs = c(0.025, 0.975))
```

The ***BF10*** **of `r sprintf("%.3f", bf10_h1)`** indicates moderate support for the null hypothesis that *wanting* is the same for the baseline and devalued conditions within subjects. The *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval_h1[1])` to `r sprintf("%.3f", credible_interval_h1[2])`.

*Delta (δ)* for the within-subject difference in wanting (acceptance bias parameter) between the baseline and devalued condition is **`r sprintf("%.3f", delta_mean)`** with a 95% Credible Interval ranging from `r sprintf("%.3f", delta_ci[1])` to `r sprintf("%.3f", delta_ci[2])`.

@fig-h1-prior-posterior below illustrates the prior and posterior density for Hypothesis 1.

```{r}
#| label: fig-h1-prior-posterior
#| fig-cap: "Prior and posterior density for Hypothesis 1."
#| fig-width: 8
#| fig-height: 6

# generate the theoretical prior density (cauchy with rscale = 1/3) across a range of delta values
delta_range <- seq(-3, 3, length.out = 1000)
prior_density <- dcauchy(delta_range, location = 0, scale = 1/3)

plot_data <- data.frame(
  delta = delta_range,
  prior = prior_density
)

# overlay empirical posterior density (from mcmc samples) against the theoretical prior
ggplot_h1 <- ggplot() +
  # posterior distribution estimated from mcmc samples
  geom_density(data = data.frame(delta = delta_samples_h1),
               aes(x = delta_samples_h1, fill = "Posterior"), 
               alpha = 0.7,
               colour = NA) +
  # prior distribution as a line
  geom_line(data = plot_data,
            aes(x = delta, y = prior, color = "Prior"),
            linewidth = 1, linetype = "twodash") +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL) +
  scale_colour_viridis_d(option = "magma", begin = 0.9, end = 0.8, name = NULL, direction = -1) +
  labs(x = "Effect size (δ)", 
       y = "Density",
       title = "") +
  scale_x_continuous(limits = c(-1,1)) +
  theme_custom() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.8),
        legend.background = element_blank(),
        legend.key = element_blank())

print(ggplot_h1)

# save high-resolution figure
ggsave(
  filename = here::here("output", "figures", "experiment2", "analyses", "fig-h1-prior-posterior.png"),
  plot = ggplot_h1,
  width = 8,
  height = 6,
  dpi = 600
)
```

@fig-h1-distribution below illustrates the distribution of the acceptance bias parameter estimated for the addiction and control groups.

```{r}
#| label: fig-h1-distribution
#| fig-cap: "Prior and posterior density for Hypothesis 1."
#| fig-width: 8
#| fig-height: 6

# pre-compute medians per condition for the median indicator points
medians <- data_params |>
  pivot_longer(cols = c(a_devalued, a_baseline),
               names_to = "condition",
               values_to = "acceptance_bias") |>
  group_by(condition) |>
  dplyr::summarise(median_val = median(acceptance_bias, na.rm = TRUE))

# density plot of the acceptance bias parameter, split by condition
ggplot_h1_dens <- data_params |>
  pivot_longer(cols = c(a_devalued, a_baseline),
               names_to = "condition",
               values_to = "acceptance_bias") |>
  ggplot2::ggplot(aes(x = acceptance_bias, fill = condition, colour = condition)) +
  ggplot2::geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  # credible interval bands positioned below the density curves
  ggdist::stat_interval(
    aes(y = -0.015),
    position = position_dodge(width = 0.02),
    orientation = "horizontal",
    linewidth = 3,
    alpha = 0.4,
    show.legend = FALSE
  ) +
  # median indicator points using pre-calculated values
  geom_point(
    data = medians,
    aes(x = median_val, y = -0.015, fill = condition, colour = condition),
    size = 2,
    shape = 19,
    alpha = 1,
    stroke = 1,
    position = position_dodge(width = 0.02, orientation = "y"),
    inherit.aes = FALSE,
    show.legend = FALSE
  ) +
  labs(x = "Wanting (α)", y = "Density", fill = "Condition") +
  scale_x_continuous(limits = c(-6, 6)) +
  theme_custom() +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("a_baseline" = "Baseline", "a_devalued" = "Devalued")) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("a_baseline" = "Baseline", "a_devalued" = "Devalued")) +
  scale_y_continuous(limits = c(-0.02, NA)) +
  theme(legend.title = element_blank(),
        legend.position = c(0.15, 0.925),
        legend.background = element_blank(),
        legend.key = element_blank()) 

print(ggplot_h1_dens)

saveRDS(ggplot_h1_dens, here::here("output", "rds", "gg_wanting_exp2.rds"))

# save high-resolution figure
ggplot2::ggsave(
  filename = here::here("output", "figures", "experiment2", "fig-h1-acceptance-bias-distribution.png"),
  plot = ggplot_h1_dens,
  width = 8,
  height = 6,
  dpi = 800
)
```

The distributions show the densities of wanting parameter estimates for the baseline (`r medians$median_val[1] |> round(3)`) and devalued condition (`r medians$median_val[2] |> round(3)`).

### Explore Hypothesis 1

We also explored whether wanting for TikTok rewards differed between the addiction and control group at baseline.

```{r}
#| label: hypothesis1-explore
#| tbl-cap: "Bayesian independent t-test for wanting (a parameter) between addiction and control groups"
#| cache: false

# bayesian independent t-test
tbf_h1_exp <- BayesFactor::ttestBF(
  x = data_params$a_baseline[data_params$group == "control"],
  y = data_params$a_baseline[data_params$group == "addiction"],
  paired = FALSE,
  rscale = 1/3
)

# extract the bayes factor (bf10)
bf10_h1_exp <- extractBF(tbf_h1_exp)$bf

# draw mcmc samples from the posterior to characterise uncertainty
posterior_samples_h1_exp <- BayesFactor::posterior(tbf_h1_exp, iterations = 10000)

# isolate the standardised effect size (delta) column from the posterior matrix
delta_samples_h1_exp <- posterior_samples_h1_exp[, "delta"]

# 95% credible interval on the effect size
credible_interval_h1_exp <- stats::quantile(posterior_samples_h1_exp[, "delta"], probs = c(0.025, 0.975))

# compute summary statistics for inline reporting
delta_mean_exp <- mean(delta_samples_h1_exp)
delta_median_exp <- median(delta_samples_h1_exp)
delta_sd_exp <- sd(delta_samples_h1_exp)
delta_ci_exp <- quantile(delta_samples_h1_exp, probs = c(0.025, 0.975))
```

The ***BF10*** **of `r sprintf("%.3f", bf10_h1_exp)`** indicates moderate support for the null hypothesis that *wanting* is the same or lower for the addiction compared to the control group. The *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval_h1_exp[1])` to `r sprintf("%.3f", credible_interval_h1_exp[2])`.

*Delta (δ)* for the between-subject difference in wanting (acceptance bias parameter) between the control and addiction group is **`r sprintf("%.3f", delta_mean_exp)`** with a 95% Credible Interval ranging from `r sprintf("%.3f", delta_ci_exp[1])` to `r sprintf("%.3f", delta_ci_exp[2])`.

```{r}
#| label: fig-h2-wanting-sensitivity-distribution

# pre-compute group medians for the median indicator points
medians <- data_params |>
  group_by(group) |>
  dplyr::summarise(median_val = median(a_baseline, na.rm = TRUE))

# density plot of devaluation sensitivity, overlaid with interval bands and median points
ggplot_h2_dens <- data_params |>
  ggplot2::ggplot(aes(x = a_baseline, fill = group, colour = group)) +
  ggplot2::geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  # add credible interval bands below the density curve
  ggdist::stat_interval(
    aes(y = -0.01),
    position = position_dodge(width = 0.0175),
    orientation = "horizontal",
    linewidth = 3,
    alpha = 0.3,
    show.legend = FALSE
  ) +
  # median points using pre-calculated values
  geom_point(
    data = medians,
    aes(x = median_val, y = -0.01, fill = group, colour = group),
    size = 2,
    shape = 19,
    alpha = 1,
    stroke = 1,
    position = position_dodge(width = 0.0175, orientation = "y"),
    inherit.aes = FALSE,
    show.legend = FALSE
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("addiction" = "Addiction", "control" = "Control")) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("addiction" = "Addiction", "control" = "Control")) +
  labs(x = "Wanting (α)", y = "Density", fill = "Condition") +
  scale_x_continuous(limits = c(-6, 6)) +
  theme_custom() +
  scale_y_continuous(limits = c(-0.02, NA)) +
  theme(legend.title = element_blank(),
        legend.position = c(0.15, 0.925),
        legend.background = element_blank(),
        legend.key = element_blank()) 

print(ggplot_h2_dens)

saveRDS(ggplot_h2_dens, here::here("output", "rds", "gg_wanting_group_exp2.rds"))

# save high-resolution figure
ggplot2::ggsave(
  filename = here::here("output", "figures", "experiment2", "fig-h2-wanting-distribution.png"),
  plot = ggplot_h2_dens,
  width = 8,
  height = 6,
  dpi = 600
)
```

## Hypothesis 2

*Hypothesis 2:* The devaluation sensitivity of *wanting* (acceptance bias parameter) is higher for the control than for the addiction group.

I perform a Bayesian paired samples t-test on the wanting-liking difference, testing for differences between the TikTok and Netflix condition within subjects.

```{r}
#| label: hypothesis2
#| tbl-cap: "Bayesian independent t-test for devaluation sensitivity between control and addiction groups"

# bayesian independent-samples t-test: between-group comparison of devaluation sensitivity
tbf_h2 <- BayesFactor::ttestBF(
  data_params$devaluation_sens[data_params$group == "control"],
  data_params$devaluation_sens[data_params$group == "addiction"],
  paired = FALSE,
  rscale = 1/3
)

# extract the bayes factor (bf10)
bf10_h2 <- extractBF(tbf_h2)$bf

# draw posterior samples
posterior_samples_h2 <- posterior(tbf_h2, iterations = 10000)

# extract delta standaridsed effect size
delta_samples_h2 <- posterior_samples_h2[, "delta"]

# extract standardised effect size (delta) and compute credible interval
credible_interval_h2 <- quantile(posterior_samples_h2[, "delta"], probs = c(0.025, 0.975))

# compute summary statistics for inline reporting
delta_mean   <- round(mean(delta_samples_h2), 3)
delta_median <- round(median(delta_samples_h2), 3)
delta_sd     <- round(sd(delta_samples_h2), 3)
delta_ci     <- round(quantile(delta_samples_h2, probs = c(0.025, 0.975)), 3)
```

The ***BF10*** **of `r sprintf("%.3f", bf10_h2)`** indicates weak support for the null hypothesis that devaluation sensitivity is the same for the control and addiction groups. The *95% Credible Interval* of the group difference ranges from `r sprintf("%.3f", credible_interval_h2[1])` to `r sprintf("%.3f", credible_interval_h2[2])`.

*Delta (δ)* for the between-subject difference in devaluation sensitivity between the control and addiction groups is **`r sprintf("%.3f", delta_mean)`** with a 95% Credible Interval ranging from `r sprintf("%.3f", delta_ci[1])` to `r sprintf("%.3f", delta_ci[2])`.

@fig-h2-prior-posterior below illustrates the prior and posterior density for Hypothesis 2.

```{r}
#| label: fig-h2-prior-posterior
#| fig-cap: "Prior and posterior density for Hypothesis 2."
#| fig-width: 8
#| fig-height: 6

# generate the theoretical cauchy prior density (rscale = 1/3) for comparison with the posterior
delta_range <- seq(-3, 3, length.out = 1000)
prior_density <- dcauchy(delta_range, location = 0, scale = 1/3)

plot_data <- data.frame(
  delta = delta_range,
  prior = prior_density
)

# overlay empirical posterior density (from mcmc samples) against the theoretical prior
ggplot_h2 <- ggplot() +
  # posterior density estimated from mcmc samples
  geom_density(data = data.frame(delta = delta_samples_h2),
               aes(x = delta_samples_h2, fill = "Posterior"), 
               alpha = 0.6,
               colour = NA) +
  # theoretical prior as a dashed line
  geom_line(data = plot_data,
            aes(x = delta, y = prior, color = "Prior"),
            linewidth = 1, linetype = "twodash") +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL) +
  scale_colour_viridis_d(option = "magma", begin = 0.9, end = 0.8, name = NULL, direction = -1) +
  labs(x = "Effect size (δ)", 
       y = "Density",
       title = "") +
  scale_x_continuous(limits = c(-1,1)) +
  scale_y_continuous(limits = c(0,6)) + 
  theme_custom() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.9),
        legend.background = element_blank(),
        legend.key = element_blank())

print(ggplot_h2)

# save high-resolution figure
ggsave(
  filename = here::here("output", "figures", "experiment2", "analyses", "fig-h2-prior-posterior.png"),
  plot = ggplot_h2,
  width = 8,
  height = 6,
  dpi = 600
)
```

```{r}
#| label: fig-h2-distribution
#| fig-cap: "Distribution of devaluation sensitivity estimates for the control and addiction group"
#| fig-width: 8
#| fig-height: 6

# pre-compute group medians for the median indicator points
medians <- data_params |>
  group_by(group) |>
  dplyr::summarise(median_val = median(devaluation_sens, na.rm = TRUE))

# density plot of devaluation sensitivity, overlaid with interval bands and median points
ggplot_h2_dens <- data_params |>
  ggplot2::ggplot(aes(x = devaluation_sens, fill = group, colour = group)) +
  ggplot2::geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  # add credible interval bands below the density curve
  ggdist::stat_interval(
    aes(y = -0.01),
    position = position_dodge(width = 0.0175),
    orientation = "horizontal",
    linewidth = 3,
    alpha = 0.3,
    show.legend = FALSE
  ) +
  # median points using pre-calculated values
  geom_point(
    data = medians,
    aes(x = median_val, y = -0.01, fill = group, colour = group),
    size = 2,
    shape = 19,
    alpha = 1,
    stroke = 1,
    position = position_dodge(width = 0.0175, orientation = "y"),
    inherit.aes = FALSE,
    show.legend = FALSE
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("addiction" = "Addiction", "control" = "Control")) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("addiction" = "Addiction", "control" = "Control")) +
  labs(x = "Devaluation sensitivity", y = "Density", fill = "Condition") +
  scale_x_continuous(limits = c(-6, 6)) +
  theme_custom() +
  scale_y_continuous(limits = c(-0.02, NA)) +
  theme(legend.title = element_blank(),
        legend.position = c(0.15, 0.925),
        legend.background = element_blank(),
        legend.key = element_blank()) 

print(ggplot_h2_dens)

saveRDS(ggplot_h2_dens, here::here("output", "rds", "gg_devaluation_sensitivity_exp2.rds"))

# save high-resolution figure
ggplot2::ggsave(
  filename = here::here("output", "figures", "experiment2", "fig-h2-devaluation-sensitivity-distribution.png"),
  plot = ggplot_h2_dens,
  width = 8,
  height = 6,
  dpi = 800
)
```

The devaluation sensitivity distributions for each group showed median values of `r medians$median_val[1] |> round(3)` (Addiction group) and `r medians$median_val[2] |> round(3)` (Control group). It appears the median devaluation sensitivity is higher in the addiction compared to the control group although this difference appears not be statistically meaningful.

To examine this, we perform a follow-up one-sided t-test directly assessing the hypothesised direction of the effect, with increased devaluation sensitivity in the addiction compared to the no-addiction group.

```{r}
#| label: hypothesis2-followup
#| tbl-cap: "Bayesian independent t-test for devaluation sensitivity between control and addiction groups"

# one-sided bayesian t-test
tbf_h2_one <- BayesFactor::ttestBF(
  data_params$devaluation_sens[data_params$group == "control"],
  data_params$devaluation_sens[data_params$group == "addiction"],
  paired = FALSE,
  rscale = 1/3,
  nullInterval = c(0, Inf) # one-sided test: only positive effect sizes are considered
)

# extract bayes factor for the one-sided alternative (index 1)
bf10_h2_one <- extractBF(tbf_h2_one)$bf

# draw posterior samples restricted to the one-sided hypothesis
posterior_samples_h2_one <- posterior(tbf_h2_one, iterations = 10000, index = 1)

# extract and summarise the standardised effect size
delta_samples_h2_one <- posterior_samples_h2_one[, "delta"]

# extract credible interval
credible_interval_h2_one <- quantile(posterior_samples_h2_one[, "delta"], probs = c(0.025, 0.975))

# compute summary statistics for inline reporting
delta_mean_one   <- round(mean(delta_samples_h2_one), 3)
delta_median_one <- round(median(delta_samples_h2_one), 3)
delta_sd_one     <- round(sd(delta_samples_h2_one), 3)
delta_ci_one     <- round(quantile(delta_samples_h2_one, probs = c(0.025, 0.975)), 3)
```

The ***BF10*** **of `r sprintf("%.3f", bf10_h2_one)`** indicates support for the one-sided null hypothesis that devaluation sensitivity is equal to or lower in the addiction compared to the control group. The median standardised effect size is **`r sprintf("%.3f", delta_median_one)`**. The *95% Credible Interval* of the effect size under the one-sided hypothesis ranges from `r sprintf("%.3f", credible_interval_h2_one[1])` to `r sprintf("%.3f", credible_interval_h2_one[2])`.

Below, I examine whether the effect (or lack thereof) changes when considering group differences in age and gender.

```{r}
#| label: multivariate-model
#| cache: false
#| warning: false
#| error: false
#| message: false

# bayesian regression model: devaluation sensitivity regressed on group membership, age, gender
model_h2_cov <- brms::brm(
  devaluation_sens ~ group + age + gender,
  data = data_params,
  family = gaussian(),
  prior = c(
    prior(cauchy(0, 0.333), class = b, coef = groupcontrol)  # matches rscale = 1/3
  ),
  cores = 4,
  chains = 4,
  iter = 10000,
  warmup = 1000,
  control = list(max_treedepth = 15, adapt_delta = 0.95)
)

# summary of posterior
print(summary(model_h2_cov), digits = 3)
```

## Hypothesis 3

*Hypothesis 3:* The devaluation sensitivity (α_baseline - α_devalued) is related to self-reported addiction severity (Bergen Social Media Addiction Scale).

I perform a Bayesian correlation using the behavioural proxy of addiction (devaluation sensitivity) and the self-reported addiction scale values for each participant.

```{r}
#| label: hypothesis3
#| tbl-cap: "Bayesian correlation between devaluation sensitivity and self-reported social media addiction"

tbf_h3 <- BayesFactor::correlationBF(
  data_params$devaluation_sens,
  data_params$bsmas_sum,
  rscale = 1/3
)

# extract bayesfactor
bf10_h3 <- extractBF(tbf_h3)$bf

# draw posterior samples
posterior_samples_h3 <- posterior(tbf_h3, iterations = 10000)

# extract rho correlation estimate
rho_samples_h3 <- posterior_samples_h3[, "rho"]

# extract credible interval
credible_interval_h3 <- quantile(posterior_samples_h3[, "rho"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
rho_mean <- round(mean(rho_samples_h3),3)
rho_median <- round(median(rho_samples_h3),3)
rho_sd <- round(sd(rho_samples_h3),3)
rho_ci <- round(quantile(rho_samples_h3, probs = c(0.025, 0.975)),3)
```

The ***BF10*** **of `r sprintf("%.3f", bf10_h3)`** indicates strong support for the null hypothesis that the devaluation sensitivity to TikTok rewards does not relate to the corresponding self-reported addiction score.

The correlation estimate is **`r sprintf("%.3f", rho_mean)`**. The *95% Credible Interval* of this correlation ranges from `r sprintf("%.3f", credible_interval_h3[1])` to `r sprintf("%.3f", credible_interval_h3[2])`.

```{r}
#| label: fig-h3-prior-posterior
#| fig-cap: "Prior and posterior density for Hypothesis 3."
#| fig-width: 8
#| fig-height: 6

# Plot prior and posterior distributions for Hypothesis 1
delta_range <- seq(-3, 3, length.out = 1000)
prior_density <- dcauchy(delta_range, location = 0, scale = 1/sqrt(3))

plot_data <- data.frame(
  delta = delta_range,
  prior = prior_density
)

ggplot_h3 <- ggplot() +
  # Posterior
  geom_density(data = data.frame(rho = rho_samples_h3),
               aes(x = rho_samples_h3, fill = "Posterior"), 
               alpha = 0.6,
               colour = NA) +
  # Prior
  geom_line(data = plot_data,
            aes(x = delta, y = prior, color = "Prior"),
            linewidth = 1, linetype = "dashed") +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL) +
  scale_colour_viridis_d(option = "magma", begin = 0.9, end = 0.8, name = NULL, direction = -1) +
  labs(x = "Effect size (ρ)", 
       y = "Density",
       title = "") + 
  scale_x_continuous(limits = c(-1,1)) +
  theme_custom() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, .85),
        legend.background = element_blank(),
        legend.key = element_blank())

print(ggplot_h3)

ggsave(
  filename = here::here("output", "figures", "experiment2", "analyses", "fig-h3-prior-posterior.png"),
  plot = ggplot_h3,
  width = 8,
  height = 6,
  dpi = 600
)

# save arranged posterior density plots
ggpubr::ggarrange(
  ggplot_h1 + labs (title = "Hypothesis 1"), 
  ggplot_h2 + labs (title = "Hypothesis 2"), 
  ggplot_h3 + labs (title = "Hypothesis 3"),
  ncol = 3, nrow = 1,
  labels = c("A", "B", "C"),
  common.legend = TRUE,
  legend = "bottom"
) |> ggsave(
  filename = here::here("output", "figures", "experiment2", "analyses", "fig-prior-posterior-arranged.png"),
  width = 18,
  height = 6,
  dpi = 600,
  bg = "white"
)
```

@fig-h3-scatter illustrates the distribution of devaluation sensitivity scores for the control and addiction groups across the range of social media addiction scores on the Bergen Social Media Addiction Scale.

```{r}
#| label: fig-h3-scatter
#| fig-cap: "Correlation between devaluation sensitivity and social media addiction scores"
#| fig-width: 8
#| fig-height: 6

# Calculate medians for each group
medians <- data_params |>
  group_by(group) |>
  dplyr::summarise(median_val = median(devaluation_sens, na.rm = TRUE))

ggplot_h3_scatt <- data_params |>
  ggplot(aes(y = bsmas_sum, x = devaluation_sens)) +

  # scatterplot with jitter for visibility
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45,
    alpha = 0.85,
    height = 0.15,
    size = 2.8,
    shape = 19,
    stroke = 0.8
  ) +
  
  # regression line - one per group
  geom_smooth(aes(group = group, color = group, fill = group),
    method = "lm", se = TRUE, show.legend = FALSE,
    linewidth = 1.2, alpha = 0.25,
    linetype = "solid"
  ) +
  # add regression equation - one per group
  ggpmisc::stat_poly_eq(
    aes(group = group, color = group,
        label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x,
    label.x = "right",
    label.y = c(0.95, 0.85),
    rr.digits = 3,
    coef.digits = 3,
    parse = TRUE,
    size = 5
  ) +

  # Enhanced color scales with transparency
      scale_fill_viridis_d(
    option = "magma",
    begin = 0.3,
    end = 0.7,
    name = NULL,
    alpha = 0.4,
    guide = "none", labels = c("addiction" = "Addiction", "control" = "Control")) +
  scale_colour_viridis_d(
    option = "magma",
    begin = 0.3,
    end = 0.7,
    name = NULL,
    guide = guide_legend(
      override.aes = list(
        size = 3.5,
        alpha = 1,
        stroke = 1.2
      )
    ), labels = c("addiction" = "Addiction", "control" = "Control")) +

  # Professional labels with units/hints if applicable
  labs(
    x = "Devaluation sensitivity",
    y = "Self-reported addiction"
  ) +

  # Improved axis scaling and breaks
  scale_x_continuous(
    breaks = seq(-6, 8, 2),
    limits = c(-6.5, 8.5),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  scale_y_continuous(
    breaks = seq(5, 30, 5),
    limits = c(4, 31),
    expand = expansion(mult = c(0.02, 0.02))
  ) +

  # Custom theme enhancements
  theme_custom() +
  theme(
    legend.position = c(0.15, 0.925),
    legend.background = element_blank(),
    legend.key = element_blank(),
  )

print(ggplot_h3_scatt)

saveRDS(ggplot_h3_scatt, here::here("output", "rds", "gg_dsbsmas_exp2.rds"))

ggplot2::ggsave(
  filename = here::here("output", "figures", "experiment2", "fig-h3-devaluation-sma-scatter.png"),
  plot = ggplot_h3_scatt,
  width = 8,
  height = 6,
  dpi = 600
)

# combined presentation of hypothesis plots
ggpubr::ggarrange(
  ggplot_h1_dens + labs(title = "Hypothesis 1") + theme(legend.position = "bottom"),
  ggplot_h2_dens + labs(title = "Hypothesis 2") + theme(legend.position = "bottom"),
  ggplot_h3_scatt + labs(title = "Hypothesis 3", x = "Addiction") + theme(
    legend.position = "bottom",
    legend.text = element_blank(),
    legend.title = element_blank()
  ) + guides(
    color = guide_legend(override.aes = list(alpha = 0, size = 0)),
    fill = guide_legend(override.aes = list(alpha = 0, size = 0))
  ),
  ncol = 3, nrow = 1,
  labels = c("A", "B", "C"),
  common.legend = FALSE
) |> ggsave(
  filename = here::here("output", "figures", "experiment2", "analyses", "fig-hypotheses-combined.png"),
  width = 18,
  height = 6,
  dpi = 800,
  bg = "white"
)
```

Likewise, we can examine the correlation between the wanting-liking dissociation for TikTok rewards observed at baseline.

```{r}
tbf_wl <- BayesFactor::correlationBF(
  data_params$wl_baseline,
  data_params$bsmas_sum,
  rscale = 1/3
)

# extract bayesfactor
bf10_wl <- extractBF(tbf_wl)$bf

# draw posterior samples
posterior_samples_wl <- posterior(tbf_wl, iterations = 10000)

# extract rho correlation estimate
rho_samples_wl <- posterior_samples_wl[, "rho"]

# extract credible interval
credible_interval_wl <- quantile(posterior_samples_wl[, "rho"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
rho_mean <- round(mean(rho_samples_wl),3)
rho_median <- round(median(rho_samples_wl),3)
rho_sd <- round(sd(rho_samples_wl),3)
rho_ci <- round(quantile(rho_samples_wl, probs = c(0.025, 0.975)),3)
```

### Wanting and self-reported addiction

```{r}
#| label: explore-wanting-bsmas
#| cache: false

# Wanting TikTok: Bayesian correlation
tbf_corr_want <- BayesFactor::correlationBF(
  data_params$a_baseline,
  data_params$bsmas_sum,
  rscale = 1/3
)

# extract the Bayes factor value
bf_want <- exp(tbf_corr_want@bayesFactor$bf)

# extract the posterior samples
posterior_samples <- BayesFactor::posterior(tbf_corr_want, iterations = 10000)

# calculate the mean of the posterior distribution for rho correlation estimate
estimated_correlation <- mean(posterior_samples[, "rho"])
estimated_correlation_med <- median(posterior_samples[, "rho"])

# get 95% credible interval
credible_interval <- quantile(posterior_samples[, "rho"], probs = c(0.025, 0.975))
```

The Bayes Factor is ***BF01*** **of `r sprintf("%.3f", bf_want)`**. The 95% Credible Interval of the correlation between the wanting parameter and self-reported addiction scores for TikTok ranges from `r sprintf("%.3f", credible_interval[1])` to `r sprintf("%.3f", credible_interval[2])`. The correlation estimate is `r sprintf("%.3f", estimated_correlation)`.

```{r}
#| label: fig-bsmas-want
#| fig-cap: "Association between Bergen Social Media Addiction Scale and Wanting"
#| fig-align: center
#| out-width: "95%"

# Calculate medians for each group
medians <- data_params |>
  group_by(group) |>
  dplyr::summarise(median_val = median(a_baseline, na.rm = TRUE))

ggplot_exp_scatt <- data_params |>
  ggplot(aes(y = bsmas_sum, x = a_baseline)) +

  # scatterplot with jitter for visibility
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45,
    alpha = 0.85,
    height = 0.15,
    size = 2.8,
    shape = 19,
    stroke = 0.8
  ) +
  
  # regression line - one per group
  geom_smooth(aes(group = group, color = group, fill = group),
    method = "lm", se = TRUE, show.legend = FALSE,
    linewidth = 1.2, alpha = 0.25,
    linetype = "solid"
  ) +
  # add regression equation - one per group
  ggpmisc::stat_poly_eq(
    aes(group = group, color = group,
        label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x,
    label.x = "right",
    label.y = c(0.95, 0.85),
    rr.digits = 3,
    coef.digits = 3,
    parse = TRUE,
    size = 5
  ) +

  # Enhanced color scales with transparency
      scale_fill_viridis_d(
    option = "magma",
    begin = 0.3,
    end = 0.7,
    name = NULL,
    alpha = 0.4,
    guide = "none", labels = c("addiction" = "Addiction", "control" = "Control")) +
  scale_colour_viridis_d(
    option = "magma",
    begin = 0.3,
    end = 0.7,
    name = NULL,
    guide = guide_legend(
      override.aes = list(
        size = 3.5,
        alpha = 1,
        stroke = 1.2
      )
    ), labels = c("addiction" = "Addiction", "control" = "Control")) +

  # Professional labels with units/hints if applicable
  labs(
    x = "Wanting",
    y = "Self-reported addiction"
  ) +

  # Improved axis scaling and breaks
  scale_x_continuous(
    breaks = seq(-6, 8, 2),
    limits = c(-6.5, 8.5),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  scale_y_continuous(
    breaks = seq(5, 30, 5),
    limits = c(4, 31),
    expand = expansion(mult = c(0.02, 0.02))
  ) +

  # Custom theme enhancements
  theme_custom() +
  theme(
    legend.position = c(0.15, 0.925),
    legend.background = element_blank(),
    legend.key = element_blank(),
  )

print(ggplot_exp_scatt)

saveRDS(ggplot_h3_scatt, here::here("output", "rds", "gg_wantingbsmas_exp2.rds"))
```

# Group Difference

Examine group differences in liking at baseline.

```{r}
#| label: group-differences-liking
#| tbl-cap: "Bayesian independent t-test for group differences in liking at baseline and devaluation"
#| warning: false
#| message: false
#| echo: false


tbf_1 <- BayesFactor::ttestBF(data_params$liking_b[data_params$group == "control"],
        data_params$liking_b[data_params$group == "addiction"],
        paired = FALSE,
        rscale = 1/3)

# extract bayesfactor
bf10_tbf <- extractBF(tbf_1)$bf

# draw posterior samples
posterior_samples <- posterior(tbf_1, iterations = 10000, index = 1)

# extract delta standaridsed effect size
delta_posterior_samples <- posterior_samples[, "delta"]

# extract credible interval
credible_interval_tbf <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
delta_mean_one   <- round(mean(delta_posterior_samples), 3)
delta_median_one <- round(median(delta_posterior_samples), 3)
delta_sd_one     <- round(sd(delta_posterior_samples), 3)
delta_ci_one     <- round(quantile(delta_posterior_samples, probs = c(0.025, 0.975)), 3)
```

Examine group differences in liking at devaluation.

```{r}
#| label: group-differences-liking-devaluation
#| tbl-cap: "Bayesian independent t-test for group differences in liking at devaluation"
#| warning: false
#| message: false
#| echo: false

tbf_2 <- BayesFactor::ttestBF(data_params$liking_d[data_params$group == "control"],
        data_params$liking_d[data_params$group == "addiction"],
        paired = FALSE,
        rscale = 1/3)

# extract bayesfactor
bf10_tbf <- extractBF(tbf_2)$bf

# draw posterior samples
posterior_samples <- posterior(tbf_2, iterations = 10000, index = 1)

# extract delta standaridsed effect size
delta_posterior_samples <- posterior_samples[, "delta"]

# extract credible interval
credible_interval_tbf <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
delta_mean_one   <- round(mean(delta_posterior_samples), 3)
delta_median_one <- round(median(delta_posterior_samples), 3)
delta_sd_one     <- round(sd(delta_posterior_samples), 3)
delta_ci_one     <- round(quantile(delta_posterior_samples, probs = c(0.025, 0.975)), 3)
```

Examine difference scores.

```{r}
#| label: group-differences-liking-diff
#| tbl-cap: "Bayesian independent t-test for group differences in liking difference scores (liking_b - liking_d)"
#| warning: false
#| message: false
#| echo: false

data_params %<>%
  dplyr::mutate(liking_diff = liking_b - liking_d) 

tbf_3 <- BayesFactor::ttestBF(data_params$liking_diff[data_params$group == "control"],
                     data_params$liking_diff[data_params$group == "addiction"],
                     paired = FALSE, rscale = 1/3)

# extract bayesfactor
bf10_tbf <- extractBF(tbf_3)$bf

# draw posterior samples
posterior_samples <- posterior(tbf_3, iterations = 10000, index = 1)

# extract delta standaridsed effect size
delta_posterior_samples <- posterior_samples[, "delta"]

# extract credible interval
credible_interval_tbf <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
delta_mean_one   <- round(mean(delta_posterior_samples), 3)
delta_median_one <- round(median(delta_posterior_samples), 3)
delta_sd_one     <- round(sd(delta_posterior_samples), 3)
delta_ci_one     <- round(quantile(delta_posterior_samples, probs = c(0.025, 0.975)), 3)
```

The Bayesfactor for the group difference in liking at baseline is **`r sprintf("%.3f", bf10_tbf)`**. The median standardised effect size is **`r sprintf("%.3f", delta_median_one)`** with a 95% Credible Interval ranging from `r sprintf("%.3f", delta_ci_one[1])` to `r sprintf("%.3f", delta_ci_one[2])`.

Next, we fit a linear regression model examining the differential effectiveness of the devaluation manipulation for the two groups, taking into consideration the group differences in liking.

```{r}
#| label: regression-devaluation-sensitivity
#| cache: false
#| warning: false
#| message: false

# devaluation sensitivity taking into consideration the liking difference effect
brms_mod <- brms::brm(
  devaluation_sens ~ group + age + liking_diff, data = data_params, family = gaussian()
)

print(summary(brms_mod), digits = 3)
```

# Replication

In a previous experiment we examined whether social media users exhibit 'incentive sensitisation' for social media rewards. To this end, we quantified the relative strength of participants' *wanting* and *liking* of TikTok and Netflix rewards. We can perform a similar analysis here by quantifying the relative strength of *wanting* and *liking* for the baseline condition.

```{r}
#| label: fig-wl-baseline
#| fig-cap: "Wanting-liking difference for TikTok rewards presented for the addicted and control group."
#| fig-width: 8
#| fig-height: 6

# apply z-transformation for consistent formatting 
a_mean <- mean(c(data_params$a_devalued, data_params$a_baseline), na.rm = TRUE)
a_sd <- sd(c(data_params$a_devalued, data_params$a_baseline), na.rm = TRUE)

# get the mean and standard deviation for liking estimates (across conditions)
strap_mean <- mean(c(data_params$liking_b, data_params$liking_d), na.rm = TRUE)
strap_sd <- sd(c(data_params$liking_b, data_params$liking_d), na.rm = TRUE)

# z-transform variables
data_params <- data_params |>
  dplyr::mutate(
    # wanting estimates
    a_devalued_z = (a_devalued - a_mean) / a_sd,
    a_baseline_z = (a_baseline - a_mean) / a_sd,
    
    # liking estimates
    strap_devalued_avg_z = (liking_d - strap_mean) / strap_sd,
    strap_baseline_avg_z = (liking_b - strap_mean) / strap_sd,
    
    # wanting liking difference
    wl_baseline_z = a_baseline_z - strap_baseline_avg_z,
    wl_devalued_z = a_devalued_z - strap_devalued_avg_z
  )

# format data to include wanting-liking dissociations
data_params %<>%
  dplyr::mutate(wl_baseline = a_baseline - liking_b,
         wl_devalued = a_devalued - liking_d)

medians <- data_params |>
  group_by(group) |>
  dplyr::summarise(median_val = median(wl_baseline_z, na.rm = TRUE))

p_wl_diff_dens <- data_params |>
  ggplot(aes(x = wl_baseline_z, fill = group)) +
  geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  ggdist::stat_interval(
    aes(y = -0.025, colour = group),
    position = position_dodge(width = 0.04),
    orientation = "horizontal",
    linewidth = 3,
    alpha = 0.3,
    show.legend = FALSE
  ) +
    geom_point(
    data = medians,
    aes(x = median_val, y = -0.025, fill = group, colour = group),
    size = 2,
    shape = 19,
    alpha = 1,
    stroke = 1,
    position = position_dodge(width = 0.04, orientation = "y"),
    inherit.aes = FALSE,
    show.legend = FALSE
  ) +
  theme_bw() +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("addiction" = "Addiction", "control" = "Control")) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL,  labels = c("addiction" = "Addiction", "control" = "Control")) +
  theme_custom() +
  scale_x_continuous(limits = c(NA, NA), breaks = seq(-4,4,1)) +
  scale_y_continuous(breaks = seq(0, 0.4, 0.1), limits = c(-0.05, 0.45)) +
  theme_custom() +
  theme(legend.title = element_blank(),
        legend.position = c(0.15, 0.925),
        legend.background = element_blank(),
        legend.key = element_blank()) +
  labs(x = "Wanting-liking dissociation (z)", y = "Density", fill = "Condition")

saveRDS(p_wl_diff_dens, here::here("output", "rds", "gg_wantlike_exp2.rds"))

print(p_wl_diff_dens)

ggplot2::ggsave(
  filename = here::here("output", "figures", "experiment2", "fig-wl-baseline-distribution.png"),
  plot = p_wl_diff_dens, width = 8, height = 6, dpi = 800, bg = "white"
)
```

@fig-wl-baseline illustrates the distribution of wanting-liking dissociation scores for the control and addiction group. Here, positive values indicate higher *wanting* than *liking*, whereas negative values indicate higher *liking* than *wanting*. The distributions of the two groups look highly similar and we furhter investigate this in the subsequent chunk.

```{r}
#| label: replication-wldifference
#| tbl-cap: "Bayesian correlation between wanting-liking dissociation and self-reported"

tbf_rep <- BayesFactor::ttestBF(data_params$wl_baseline[data_params$group == "control"],
                     data_params$wl_baseline[data_params$group == "addiction"],
                     paired = FALSE, rscale = 1/3)

# extract bayesfactor
bf10_tbf <- extractBF(tbf_rep)$bf

# draw posterior samples
posterior_samples <- posterior(tbf_rep, iterations = 10000, index = 1)

# extract delta standaridsed effect size
delta_posterior_samples <- posterior_samples[, "delta"]

# extract credible interval
credible_interval_tbf <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
delta_mean   <- round(mean(delta_posterior_samples), 3)
delta_median <- round(median(delta_posterior_samples), 3)
delta_sd     <- round(sd(delta_posterior_samples), 3)
delta_ci     <- round(quantile(delta_posterior_samples, probs = c(0.025, 0.975)), 3)
```

The Bayesfactor for the correlation between the wanting-liking dissociation at baseline and the self-reported addiction score is **`r sprintf("%.3f", bf10_tbf)`**. The median standardised effect size is **`r sprintf("%.3f", delta_median)`** with a 95% Credible Interval ranging from `r sprintf("%.3f", delta_ci[1])` to `r sprintf("%.3f", delta_ci[2])`.

Next, I visualised the correlation between these scores and the self-reported TikTok addiction (BSMAS)

```{r}
gg_wlbsmas_exp2 <- data_params |>
  ggplot(aes(y = bsmas_sum, x = wl_baseline_z)) +

  # scatterplot with jitter for visibility
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45,
    alpha = 0.85,
    height = 0.15,
    size = 2.8,
    shape = 19,
    stroke = 0.8
  ) +
  
    # regression line - one per group
  geom_smooth(aes(group = group, color = group, fill = group),
    method = "lm", se = TRUE, show.legend = FALSE,
    linewidth = 1.2, alpha = 0.25,
    linetype = "solid"
  ) +
  # add regression equation - one per group
  ggpmisc::stat_poly_eq(
    aes(group = group, color = group,
        label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x,
    label.x = "right",
    label.y = c(0.95, 0.85),
    rr.digits = 3,
    coef.digits = 3,
    parse = TRUE,
    size = 5
  ) +
  scale_colour_viridis_d(
    option = "magma", begin = 0.3, end = 0.7, name = NULL, labels = c("addiction" = "Addiction", "control" = "Control")) +
  scale_fill_viridis_d(
    option = "magma", begin = 0.3, end = 0.7,
    name = NULL, guide = "none", labels = c("addiction" = "Addiction", "control" = "Control")) +
  labs(x = "Wanting-liking dissociation (z)", y = "Self-reported addiction") +
  scale_y_continuous(breaks = seq(5, 30, 5), limits = c(4, 31), expand = expansion(mult = c(0.02, 0.02))) +
  theme_custom() +
  theme(legend.position = c(0.15, 0.925), legend.background = element_blank(), legend.key = element_blank())

saveRDS(gg_wlbsmas_exp2, here::here("output", "rds", "gg_wlbsmas_exp2.rds"))

```

```{r}
#|label: wl-explore-ttest

#| label: wl-bayesian-results
#| tbl-cap: "Bayesian independent t-test results"

# bayesian independent ttest
tbf_diff <- BayesFactor::ttestBF(
  data_params$wl_baseline[data_params$group == "control"],
  data_params$wl_baseline[data_params$group == "addiction"],
  paired = FALSE,
  rscale = 1/3
)

bf <- exp(tbf_diff@bayesFactor$bf)
posterior <- BayesFactor::posterior(tbf_diff, iterations = 10000)
delta <- as.vector(posterior[, "delta"])

# results to demonstrate in table
results <- data.frame(
  `Bayes Factor (BF₁₀)` = sprintf("%.3f", bf),
  `Effect Size (δ)` = sprintf("%.3f", mean(delta)),
  `95% CI` = sprintf("[%.3f, %.3f]", 
                     quantile(delta, 0.025), 
                     quantile(delta, 0.975)),
  `P(δ > 0.2)` = sprintf("%.3f%%", mean(delta > 0.2) * 100),
  check.names = FALSE
)

# table output
knitr::kable(results, align = "c") |>
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "condensed"),
    full_width = FALSE,
    position = "center"
  )
```

We further examine other potential correlates of the wanting-liking association.

```{r}
tbf_exp1 <- BayesFactor::correlationBF(
  data_params$wl_baseline,
  data_params$bisr21_sum,
  rscale = 1/3
)

# extract bayesfactor
bf10_exp1 <- extractBF(tbf_exp1)$bf

# draw posterior samples
posterior_samples_exp1 <- posterior(tbf_exp1, iterations = 10000)

# extract rho correlation estimate
rho_samples_exp1 <- posterior_samples_exp1[, "rho"]

# extract credible interval
credible_interval_exp1 <- quantile(posterior_samples_exp1[, "rho"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
rho_mean <- round(mean(rho_samples_exp1),3)
rho_median <- round(median(rho_samples_exp1),3)
rho_sd <- round(sd(rho_samples_exp1),3)
rho_ci <- round(quantile(rho_samples_exp1, probs = c(0.025, 0.975)),3)
```

The ***BF10*** **of `r sprintf("%.3f", bf10_exp1)`** indicates strong support for the null hypothesis that the wanting-liking dissociation at baseline does not relate to the corresponding self-reported impulsivity score. The correlation estimate is **`r sprintf("%.3f", rho_mean)`**. The 95% Credible Interval of this correlation ranges from `r sprintf("%.3f", credible_interval_exp1[1])` to `r sprintf("%.3f", credible_interval_exp1[2])`.

#### Condition differences in computational parameters

##### Reward sensitivity

```{r}
tbf <- BayesFactor::ttestBF(
  data_params$kR_baseline,
  data_params$kR_devalued,
  paired = TRUE,
  rscale = 1/3,
)

bf <- exp(tbf@bayesFactor$bf)

# extract the posterior samples
posterior_samples <- BayesFactor::posterior(tbf, iterations = 10000)

# calculate the mean of the posterior distribution for delta
estimated_correlation <- mean(posterior_samples[, "delta"])
estimated_correlation_med <- median(posterior_samples[, "delta"])

# get 95% credible interval
credible_interval <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

tbf_chains <- BayesFactor::posterior(tbf, iterations = 10000)
base::summary(tbf_chains)
plot(tbf_chains[, "delta"])
```

The ***BF01*** **of `r round(bf, 3)`** indicates strong support for the alternative hypothesis that *reward sensitivity* does differ between the baseline and devalued conditions within subjects. The *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval[1])` to `r sprintf("%.3f", credible_interval[2])`.

##### Effort sensitivity

```{r}
tbf <- BayesFactor::ttestBF(
  data_params$kE_baseline,
  data_params$kE_devalued,
  paired = TRUE,
  rscale = 1/3,
)

bf <- exp(tbf@bayesFactor$bf)

# extract the posterior samples
posterior_samples <- BayesFactor::posterior(tbf, iterations = 10000)

# calculate the mean of the posterior distribution for delta
estimated_correlation <- mean(posterior_samples[, "delta"])
estimated_correlation_med <- median(posterior_samples[, "delta"])

# get 95% credible interval
credible_interval <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

tbf_chains <- BayesFactor::posterior(tbf, iterations = 10000)
base::summary(tbf_chains)
plot(tbf_chains[, "delta"])
```

The ***BF01*** **of `r round(bf, 3)`** indicates weak support for the null hypothesis that *effort sensitivity* does not differ between the TikTok and Netflix conditions within subjects. The *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval[1])` to `r sprintf("%.3f", credible_interval[2])`.

```{r}
#| label: fig-difference-params
#| fig-cap: "Distributions of effort and reward sensitivity parameters for TikTok and Netflix"
#| fig-align: center
#| out-width: "95%"

p_eff <- data_params |>
  # create a longer format dataset that includes both baseline and devalued data
  tidyr::pivot_longer(
    cols = c(kE_baseline, kE_devalued),
    names_to = "condition_ke",
    values_to = "effort_sensitivity"
  ) |>
  # create plot
  ggplot2::ggplot(aes(x = effort_sensitivity, fill = condition_ke)) +
  geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  theme_bw() +
  scale_fill_viridis_d(
    option = "magma", begin = 0.3, end = 0.7, name = NULL,
    labels = c("kE_baseline" = "Baseline", "kE_devalued" = "Devalued")
  ) + 
  scale_x_continuous(breaks = seq(0,1,.2), limits = c(0,1)) +
  scale_y_continuous(breaks = seq(0,2,.5)) +
  theme(legend.position="right", legend.direction = "vertical") + 
  labs(x = "Effort sensitivity", y = "Density", fill = "Condition") 

p_rew <- data_params |>
  # create a longer format dataset that includes both baseline and devalued data
  tidyr::pivot_longer(
    cols = c(kR_baseline, kR_devalued),
    names_to = "condition_kr",
    values_to = "reward_sensitivity"
  ) |>
  # create plot
  ggplot2::ggplot(aes(x = reward_sensitivity, fill = condition_kr)) +
  geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  theme_bw() +
  scale_fill_viridis_d(
    option = "magma", begin = 0.3, end = 0.7, name = NULL,
    labels = c("kR_baseline" = "Baseline", "kR_devalued" = "Devalued")
  ) +
  scale_x_continuous(breaks = seq(0,6,1), limits = c(0, 6)) +
  scale_y_continuous(breaks = seq(0,1,.2), limits = c(0,0.6)) +
  labs(x = "Reward sensitivity", y = "Density", fill = "Condition")

# create combined plot
combined_plot <- ggpubr::ggarrange(
  p_rew, p_eff,
  ncol = 2,
  labels = c("C", "D"),
  common.legend = TRUE,
  legend = "right"
)

saveRDS(combined_plot, file = here::here("output", "rds", "kekr_parameter_distributions_exp2.rds"))

# save the main plot without legend
ggplot2::ggsave(
  filename = "kekr_parameter_distributions.png", 
  plot = combined_plot, 
  path = here::here("output", "figures", "experiment2"),
  dpi = 800, width = 10, height = 5, bg = "white"
)
```

Likewise, we can examine differences in free parameters between the self-reported addiction and control group.

##### Reward sensitivity

```{r}
tbf <- BayesFactor::ttestBF(
  data_params$kR_baseline[data_params$group == "control"],
  data_params$kR_baseline[data_params$group == "addiction"],
  paired = FALSE,
  rscale = 1/3,
)

bf <- exp(tbf@bayesFactor$bf)

# extract the posterior samples
posterior_samples <- BayesFactor::posterior(tbf, iterations = 10000)

# calculate the mean of the posterior distribution for delta
estimated_correlation <- mean(posterior_samples[, "delta"])
estimated_correlation_med <- median(posterior_samples[, "delta"])

# get 95% credible interval
credible_interval <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

tbf_chains <- BayesFactor::posterior(tbf, iterations = 10000)
base::summary(tbf_chains)
plot(tbf_chains[, "delta"])
```

The ***BF01*** **of `r round(bf, 3)`** indicates support for the null hypothesis that *reward sensitivity* does not differ between the addiction and control group at baseline. The *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval[1])` to `r sprintf("%.3f", credible_interval[2])`.

##### Effort sensitivity

```{r}
tbf <- BayesFactor::ttestBF(
  data_params$kE_baseline[data_params$group == "addiction"],
  data_params$kE_baseline[data_params$group == "control"],
  paired = FALSE,
  rscale = 1/3,
)

bf <- exp(tbf@bayesFactor$bf)

# extract the posterior samples
posterior_samples <- BayesFactor::posterior(tbf, iterations = 10000)

# calculate the mean of the posterior distribution for delta
estimated_correlation <- mean(posterior_samples[, "delta"])
estimated_correlation_med <- median(posterior_samples[, "delta"])

# get 95% credible interval
credible_interval <- quantile(posterior_samples[, "delta"], probs = c(0.025, 0.975))

tbf_chains <- BayesFactor::posterior(tbf, iterations = 10000)
base::summary(tbf_chains)
plot(tbf_chains[, "delta"])
```

The ***BF01*** **of `r round(bf, 3)`** indicates strong support for the null hypothesis that *effort sensitivity* does not differ between the addiction and control groups. The *95% Credible Interval* of the condition difference ranges from `r sprintf("%.3f", credible_interval[1])` to `r sprintf("%.3f", credible_interval[2])`.

```{r}
#| label: fig-difference-params-kekr
#| fig-cap: "Distributions of effort and reward sensitivity parameters for TikTok and Netflix"
#| fig-align: center
#| out-width: "95%"

p_eff <- data_params |>
  # create a longer format dataset that includes both baseline and devalued data
  tidyr::pivot_longer(
    cols = c(kE_baseline, kE_devalued),
    names_to = "condition_ke",
    values_to = "effort_sensitivity"
  ) |>
  # create plot
  ggplot2::ggplot(aes(x = effort_sensitivity, fill = condition_ke)) +
  geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  theme_bw() +
  scale_fill_viridis_d(
    option = "magma", begin = 0.3, end = 0.7, name = NULL,
    labels = c("kE_baseline" = "Baseline", "kE_devalued" = "Devalued")
  ) + 
  scale_x_continuous(breaks = seq(0,1,.2), limits = c(0,1)) +
  scale_y_continuous(breaks = seq(0,2,.5)) +
  theme(legend.position="right", legend.direction = "vertical") + 
  labs(x = "Effort sensitivity", y = "Density", fill = "Condition") 

p_rew <- data_params |>
  # create a longer format dataset that includes both baseline and devalued data
  tidyr::pivot_longer(
    cols = c(kR_baseline, kR_devalued),
    names_to = "condition_kr",
    values_to = "reward_sensitivity"
  ) |>
  # create plot
  ggplot2::ggplot(aes(x = reward_sensitivity, fill = condition_kr)) +
  geom_density(alpha = .7, outline.type = "lower", colour = NA) +
  theme_bw() +
  scale_fill_viridis_d(
    option = "magma", begin = 0.3, end = 0.7, name = NULL,
    labels = c("kR_baseline" = "Baseline", "kR_devalued" = "Devalued")
  ) +
  scale_x_continuous(breaks = seq(0,6,1), limits = c(0, 6)) +
  scale_y_continuous(breaks = seq(0,1,.2), limits = c(0,0.6)) +
  labs(x = "Reward sensitivity", y = "Density", fill = "Condition")

# create combined plot
combined_plot <- ggpubr::ggarrange(
  p_rew, p_eff,
  ncol = 2,
  labels = c("C", "D"),
  common.legend = TRUE,
  legend = "right"
)

saveRDS(combined_plot, file = here::here("output", "rds", "kekr_parameter_distributions_exp2.rds"))

# save the main plot without legend
ggplot2::ggsave(
  filename = "kekr_parameter_distributions.png", 
  plot = combined_plot, 
  path = here::here("output", "figures", "experiment2"),
  dpi = 800, width = 10, height = 5, bg = "white"
)

combined_plot
```



### Self-reported addiction correlates

Below, we examine correlations between other computational parameters (effort sensitivity, reward sensitivity) and self-reported levels of social media addiction (TikTok, BSMAS).

We use Bayesian correlations to examine the above.

```{r}
tbf <- BayesFactor::correlationBF(
  data_params$kR_baseline,
  data_params$bsmas_sum,
  rscale = 1/3
)

# extract bayesfactor
bf10 <- extractBF(tbf)$bf

# draw posterior samples
posterior_samples <- posterior(tbf, iterations = 10000)

# extract rho correlation estimate
rho_samples <- posterior_samples[, "rho"]

# extract credible interval
credible_interval <- quantile(posterior_samples[, "rho"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
rho_mean <- round(mean(rho_samples),3)
rho_median <- round(median(rho_samples),3)
rho_sd <- round(sd(rho_samples),3)
rho_ci <- round(quantile(rho_samples, probs = c(0.025, 0.975)),3)
```

```{r}
tbf <- BayesFactor::correlationBF(
  data_params$kE_baseline,
  data_params$bsmas_sum,
  rscale = 1/3
)

# extract bayesfactor
bf10 <- extractBF(tbf)$bf

# draw posterior samples
posterior_samples <- posterior(tbf, iterations = 10000)

# extract rho correlation estimate
rho_samples <- posterior_samples[, "rho"]

# extract credible interval
credible_interval <- quantile(posterior_samples[, "rho"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
rho_mean <- round(mean(rho_samples),3)
rho_median <- round(median(rho_samples),3)
rho_sd <- round(sd(rho_samples),3)
rho_ci <- round(quantile(rho_samples, probs = c(0.025, 0.975)),3)
```

Same correlations as above but for the devalued condition.

```{r}
tbf <- BayesFactor::correlationBF(
  data_params$kR_devalued,
  data_params$bsmas_sum,
  rscale = 1/3
)

# extract bayesfactor
bf10 <- extractBF(tbf)$bf

# draw posterior samples
posterior_samples <- posterior(tbf, iterations = 10000)

# extract rho correlation estimate
rho_samples <- posterior_samples[, "rho"]

# extract credible interval
credible_interval <- quantile(posterior_samples[, "rho"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
rho_mean <- round(mean(rho_samples),3)
rho_median <- round(median(rho_samples),3)
rho_sd <- round(sd(rho_samples),3)
rho_ci <- round(quantile(rho_samples, probs = c(0.025, 0.975)),3)
```

```{r}
tbf <- BayesFactor::correlationBF(
  data_params$kE_devalued,
  data_params$bsmas_sum,
  rscale = 1/3
)

# extract bayesfactor
bf10 <- extractBF(tbf)$bf

# draw posterior samples
posterior_samples <- posterior(tbf, iterations = 10000)

# extract rho correlation estimate
rho_samples <- posterior_samples[, "rho"]

# extract credible interval
credible_interval <- quantile(posterior_samples[, "rho"], probs = c(0.025, 0.975))

# compute posterior statistics from samples
rho_mean <- round(mean(rho_samples),3)
rho_median <- round(median(rho_samples),3)
rho_sd <- round(sd(rho_samples),3)
rho_ci <- round(quantile(rho_samples, probs = c(0.025, 0.975)),3)
```

#### Visualisations

```{r}

# acceptance bias (baseline)
ggplot_a_base <- data_params |>
  ggplot(aes(x = bsmas_sum, y = a_baseline)) +
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45, alpha = 0.85, height = 0.15, size = 2.8, shape = 19, stroke = 0.8
  ) +
  geom_smooth(aes(group = 1),
    method = "lm", se = TRUE, show.legend = FALSE,
    color = "gray15", fill = "gray30", linewidth = 1.2, alpha = 0.25, linetype = "solid"
  ) +
  ggpmisc::stat_poly_eq(
    aes(group = 1, label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x, label.x = "right", label.y = "top", rr.digits = 3,
    coef.digits = 3, parse = TRUE, size = 5
  ) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = "Group", labels = c("Addiction", "No Addiction"),
                         guide = guide_legend(override.aes = list(size = 3.5, alpha = 1, stroke = 1.2))
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, alpha = 0.4, guide = "none") +
  labs(x = "Self-reported addiction", y = "Wanting (b)") +
  scale_y_continuous(breaks = seq(-6, 8, 2), limits = c(-6.5, 8.5), expand = expansion(mult = c(0.02, 0.02))) +
  scale_x_continuous(breaks = seq(5, 30, 5), limits = c(4, 31), expand = expansion(mult = c(0.02, 0.02))) +
  theme_custom() +
  theme(legend.position = c(0.86, 0.80), legend.background = element_blank(), legend.key = element_blank())

# acceptance bias (devalued)
ggplot_a_deval <- data_params |>
  ggplot(aes(x = bsmas_sum, y = a_devalued)) +
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45, alpha = 0.85, height = 0.15, size = 2.8, shape = 19, stroke = 0.8
  ) +
  geom_smooth(aes(group = 1),
    method = "lm", se = TRUE, show.legend = FALSE,
    color = "gray15", fill = "gray30", linewidth = 1.2, alpha = 0.25, linetype = "solid"
  ) +
  ggpmisc::stat_poly_eq(
    aes(group = 1, label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x, label.x = "right", label.y = "top", rr.digits = 3,
    coef.digits = 3, parse = TRUE, size = 5
  ) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, 
                         guide = guide_legend(override.aes = list(size = 3.5, alpha = 1, stroke = 1.2))
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, alpha = 0.4, guide = "none") +
  labs(x = "Self-reported addiction", y = "Wanting (d)") +
  scale_y_continuous(breaks = seq(-6, 8, 2), limits = c(-6.5, 8.5), expand = expansion(mult = c(0.02, 0.02))) +
  scale_x_continuous(breaks = seq(5, 30, 5), limits = c(4, 31), expand = expansion(mult = c(0.02, 0.02))) +
  theme_custom() +
  theme(legend.position = c(0.86, 0.80), legend.background = element_blank(), legend.key = element_blank()) 

# reward sensitivity (baseline)
ggplot_kr_base <- data_params |>
  ggplot(aes(x = bsmas_sum, y = kR_baseline)) +
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45, alpha = 0.85, height = 0.15, size = 2.8, shape = 19, stroke = 0.8
  ) +
  geom_smooth(aes(group = 1),
    method = "lm", se = TRUE, show.legend = FALSE,
    color = "gray15", fill = "gray30", linewidth = 1.2, alpha = 0.25, linetype = "solid"
  ) +
  ggpmisc::stat_poly_eq(
    aes(group = 1, label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x, label.x = "right", label.y = "top", rr.digits = 3,
    coef.digits = 3, parse = TRUE, size = 5
  ) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, 
                         guide = guide_legend(override.aes = list(size = 3.5, alpha = 1, stroke = 1.2))
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, alpha = 0.4, guide = "none") +
  labs(x = "Self-reported addiction", y = "Reward sensitivity (b)") +
  scale_y_continuous(breaks = seq(0, 6, 1), limits = c(0, 6), expand = expansion(mult = c(0.02, 0.02))) +
  scale_x_continuous(breaks = seq(5, 30, 5), limits = c(4, 31), expand = expansion(mult = c(0.02, 0.02))) +
  theme_custom() +
  theme(legend.position = c(0.86, 0.80), legend.background = element_blank(), legend.key = element_blank()) 


# reward sensitivity (devalued)
ggplot_kr_deval <- data_params |>
  ggplot(aes(x = bsmas_sum, y = kR_devalued)) +
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45, alpha = 0.85, height = 0.15, size = 2.8, shape = 19, stroke = 0.8
  ) +
  geom_smooth(aes(group = 1),
    method = "lm", se = TRUE, show.legend = FALSE,
    color = "gray15", fill = "gray30", linewidth = 1.2, alpha = 0.25, linetype = "solid"
  ) +
  ggpmisc::stat_poly_eq(
    aes(group = 1, label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x, label.x = "right", label.y = "top", rr.digits = 3,
    coef.digits = 3, parse = TRUE, size = 5
  ) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, 
                         guide = guide_legend(override.aes = list(size = 3.5, alpha = 1, stroke = 1.2))
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, alpha = 0.4, guide = "none") +
  labs(x = "Self-reported addiction", y = "Reward sensitivity (d)") +
  scale_y_continuous(breaks = seq(0, 6, 1), limits = c(0, 6), expand = expansion(mult = c(0.02, 0.02))) +
  scale_x_continuous(breaks = seq(5, 30, 5), limits = c(4, 31), expand = expansion(mult = c(0.02, 0.02))) +
  theme_custom() +
  theme(legend.position = c(0.86, 0.80), legend.background = element_blank(), legend.key = element_blank())

# effort sensitivity (baseline)
ggplot_ke_base <- data_params |>
  ggplot(aes(x = bsmas_sum, y = kE_baseline)) +
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45, alpha = 0.85, height = 0.15, size = 2.8, shape = 19, stroke = 0.8
  ) +
  geom_smooth(aes(group = 1),
    method = "lm", se = TRUE, show.legend = FALSE,
    color = "gray15", fill = "gray30", linewidth = 1.2, alpha = 0.25, linetype = "solid"
  ) +
  ggpmisc::stat_poly_eq(
    aes(group = 1, label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x, label.x = "right", label.y = "top", rr.digits = 3,
    coef.digits = 3, parse = TRUE, size = 5
  ) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, 
                         guide = guide_legend(override.aes = list(size = 3.5, alpha = 1, stroke = 1.2))
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, alpha = 0.4, guide = "none") +
  labs(x = "Self-reported addiction", y = "Effort sensitivity (b)") +
  scale_y_continuous(breaks = seq(0, 1.5, .25), limits = c(0, 1.5), expand = expansion(mult = c(0.02, 0.02))) +
  scale_x_continuous(breaks = seq(5, 30, 5), limits = c(4, 31), expand = expansion(mult = c(0.02, 0.02))) +
  theme_custom() +
  theme(legend.position = c(0.86, 0.80), legend.background = element_blank(), legend.key = element_blank()) 

# reward sensitivity (devalued)
ggplot_ke_deval <- data_params |>
  ggplot(aes(x = bsmas_sum, y = kE_devalued)) +
  geom_jitter(aes(fill = group, colour = group),
    width = 0.45, alpha = 0.85, height = 0.15, size = 2.8, shape = 19, stroke = 0.8
  ) +
  geom_smooth(aes(group = 1),
    method = "lm", se = TRUE, show.legend = FALSE,
    color = "gray15", fill = "gray30", linewidth = 1.2, alpha = 0.25, linetype = "solid"
  ) +
  ggpmisc::stat_poly_eq(
    aes(group = 1, label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    formula = y ~ x, label.x = "right", label.y = "top", rr.digits = 3,
    coef.digits = 3, parse = TRUE, size = 5
  ) +
  scale_colour_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, 
                         guide = guide_legend(override.aes = list(size = 3.5, alpha = 1, stroke = 1.2))
  ) +
  scale_fill_viridis_d(option = "magma", begin = 0.3, end = 0.7, name = NULL, alpha = 0.4, guide = "none") +
  labs(x = "Self-reported addiction", y = "Effort sensitivity (d)") +
  scale_y_continuous(breaks = seq(0, 1.5, .25), limits = c(0, 1.5), expand = expansion(mult = c(0.02, 0.02))) +
  scale_x_continuous(breaks = seq(5, 30, 5), limits = c(4, 31), expand = expansion(mult = c(0.02, 0.02))) +
  theme_custom() +
  theme(legend.position = c(0.86, 0.80), legend.background = element_blank(), legend.key = element_blank())

# add plot margins

legend <- ggpubr::get_legend(ggplot_a_base + theme(legend.position = "bottom", legend.direction = "horizontal"))

a_base_m <- ggMarginal(ggplot_a_base + theme(legend.position = "none", axis.title.x = element_blank()),
                       type = "density", groupColour = FALSE, groupFill = TRUE, margins = "y", alpha = .9, colour = NA)
a_deval_m <- ggMarginal(ggplot_a_deval + theme(legend.position = "none"), 
                        type = "density", groupColour = FALSE, groupFill = TRUE, margins = "y", alpha = .9, colour = NA)
kr_base_m <- ggMarginal(ggplot_kr_base + theme(legend.position = "none", axis.title.x = element_blank()),
                        type = "density", groupColour = FALSE, groupFill = TRUE, margins = "y", alpha = .9, colour = NA)
kr_deval_m <- ggMarginal(ggplot_kr_deval + theme(legend.position = "none"), 
                         type = "density", groupColour = FALSE, groupFill = TRUE, margins = "y", alpha = .9, colour = NA)
ke_base_m <- ggMarginal(ggplot_ke_base + theme(legend.position = "none", axis.title.x = element_blank()),
                        type = "density", groupColour = FALSE, groupFill = TRUE, margins = "y", alpha = .9, colour = NA)
ke_deval_m <- ggMarginal(ggplot_ke_deval + theme(legend.position = "none"), 
                         type = "density", groupColour = FALSE, groupFill = TRUE, margins = "y", alpha = .9, colour = NA)

# arrange plots
plots <- cowplot::plot_grid(
  ggplotify::as.ggplot(a_base_m),
  ggplotify::as.ggplot(kr_base_m),
  ggplotify::as.ggplot(ke_base_m),
  ggplotify::as.ggplot(a_deval_m),
  ggplotify::as.ggplot(kr_deval_m),
  ggplotify::as.ggplot(ke_deval_m),
  ncol = 3, nrow = 2,
  labels = c("A", "B", "C", "D", "E", "F"),
  label_fontface = "bold"
)

# add legend
combined <- cowplot::plot_grid(
  plots,
  legend,
  ncol = 1,
  rel_heights = c(1, 0.08)
)

ggsave(
  filename = "parameter_sma_correlations.png",
  plot = combined,
  path = here::here("output", "figures", "experiment2"),
  dpi = 800, width = 10, height = 6, bg = "white"
)

plots
```
