---
title: "Sensitivity Analyses"
description: "This document includes the documentation of the performed sensitivity analyses for the winning parabolic effort-based decision-making model with three free parameters."
author:
  - name: Lukas Gunschera
    orcid: 0000-0002-8241-0833
    email: l.gunschera@outlook.com
    corresponding: true
    affiliation:
      - ref: 1
affiliations:
  - id: 1
    name: University of Cambridge
    department: Medical Research Council Cognition and Brain Sciences Unit
format:
  html:
    code-fold: true
    toc: true
editor: visual
---

```{r}
#| label: Setup-document
#| include: false
#| message: false
#| cache: false

# Output options
is_html <- knitr::is_html_output()
knitr::opts_chunk$set(
  eval = TRUE,
  cache = FALSE,  # disable global caching by default
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  echo = is_html,
  fig.width = 7,
  fig.height = 5,
  dpi = 300,
  dev = "ragg_png"  # ragg_png for better performance
)

source(here::here("code", "00_setup.R"))
set.seed(777)

library(renv) # load renv package
renv::restore(project = here::here()) # restore the environment

# load dependencies
pacman::p_load(gt, zoo, plm, brms, ragg, here, knitr, purrr, dplyr, tidyr, ggpubr, scales, viridis, moments, stringr, rstatix, janitor, ggplot2, ggExtra, rstanarm, gtExtras, cmdstanr, magrittr, hBayesDM, patchwork, ggpattern, bayesplot, tidybayes, lubridate, posterior, bayestestR, BayesFactor, bridgesampling)

# load custom dependencies
source(here::here("code", "experiment1", "functions", "fun_plots.R"))
source(here::here("code", "experiment1", "functions", "fun_helper.R"))
source(here::here("code", "experiment1", "functions", "fun_fit_models.R"))
source(here::here("code", "experiment1", "functions", "fun_model_preprocess.R"))
source(here::here("code", "experiment1", "functions", "fun_modeling_cleandata.R"))
source(here::here("code", "experiment1", "functions", "fun_parameter_estimates.R"))
source(here::here("code", "experiment1", "functions", "fun_posterior_predictions.R"))
source(here::here("code", "experiment1", "functions", "fun_model_convergence_check.R"))

viridis_colors <- viridis::viridis(4, option = "magma", begin = 0.3, end = 0.7)
condition_colors <- viridis::viridis(2, option = "magma", begin = 0.3, end = 0.7)
```

```{r}
cat("Document rendered at:", format(Sys.time(), "%Y-%m-%d %H:%M:%S"))
```

## Data

Load the pocessed participant data as returned from the script 'code/sma_dataprocessing.R'. Note, the current script depends on you running the sma_dataprocessing.R script prior in order to access the returned data object. This is to reduce computational demands and redundancies.

```{r}
#| label: data import

data_params <- readRDS(here::here("data", "experiment1", "modelling", "parameters", "m3_para_data.RDS"))

# get subject identifier of participant reading magazines
p_excl <- data_params |> dplyr::filter(watch_netflix_compliance_text == "I also go through the magazines briefly") |> pull(subj_id)

# exclude participants based on compliance violations
data_main <- data_params |>
  dplyr::filter(watch_tiktok_compliance == TRUE) |> # exclude TikTok non-compliers
  dplyr::filter(subj_id != p_excl) # exclude Netflix non-compliers
```

Compute the descriptive statistics for the parameters based on which the *wanting-liking difference* is estimated. This helps us gauge appropriate prior distributions for later statistical analyses.

```{r}
#|label: z-tranform

# get the mean and standard deviation for wanting estimates (across conditions)
a_mean <- mean(c(data_params$a_netflix, data_params$a_tiktok), na.rm = TRUE)
a_sd <- sd(c(data_params$a_netflix, data_params$a_tiktok), na.rm = TRUE)

# get the mean and standard deviation for liking estimates (across conditions)
strap_mean <- mean(c(data_params$strap_netflix_avg, data_params$strap_tiktok_avg), na.rm = TRUE)
strap_sd <- sd(c(data_params$strap_netflix_avg, data_params$strap_tiktok_avg), na.rm = TRUE)

# z-transform variables
data_params <- data_params |>
  dplyr::mutate(
    # wanting estimates
    a_netflix_z = (a_netflix - a_mean) / a_sd,
    a_tiktok_z = (a_tiktok - a_mean) / a_sd,
    
    # liking estimates
    strap_netflix_avg_z = (strap_netflix_avg - strap_mean) / strap_sd,
    strap_tiktok_avg_z = (strap_tiktok_avg - strap_mean) / strap_sd,
    
    # wanting liking difference
    wl_tiktok_z = a_tiktok_z - strap_tiktok_avg_z,
    wl_netflix_z = a_netflix_z - strap_netflix_avg_z
  )

## Transformation for main dataset (incl. compliance exclusions)

# get the mean and standard deviation for wanting estimates (across conditions)
a_mean <- mean(c(data_main$a_netflix, data_main$a_tiktok), na.rm = TRUE)
a_sd <- sd(c(data_main$a_netflix, data_main$a_tiktok), na.rm = TRUE)

# get the mean and standard deviation for liking estimates (across conditions)
strap_mean <- mean(c(data_main$strap_netflix_avg, data_main$strap_tiktok_avg), na.rm = TRUE)
strap_sd <- sd(c(data_main$strap_netflix_avg, data_main$strap_tiktok_avg), na.rm = TRUE)

# z-transform variables
data_main <- data_main |>
  dplyr::mutate(
    # wanting estimates
    a_netflix_z = (a_netflix - a_mean) / a_sd,
    a_tiktok_z = (a_tiktok - a_mean) / a_sd,
    
    # liking estimates
    strap_netflix_avg_z = (strap_netflix_avg - strap_mean) / strap_sd,
    strap_tiktok_avg_z = (strap_tiktok_avg - strap_mean) / strap_sd,
    
    # wanting liking difference
    wl_tiktok_z = a_tiktok_z - strap_tiktok_avg_z,
    wl_netflix_z = a_netflix_z - strap_netflix_avg_z
  )
```

The above code adds the z-transformed scores for *wanting* and *liking* as per the mean and standard deviation of the estimates across conditions.

```{r}
#| label: descriptive statistics

# select subset of variables
vars_of_interest <- c("a_tiktok", "a_tiktok_z", "a_netflix", "a_netflix_z", "strap_tiktok_avg", "strap_tiktok_avg_z", "strap_netflix_avg", "strap_netflix_avg_z", "wl_tiktok", "wl_netflix", "wl_tiktok_z", "wl_netflix_z")

# format long wanting data for plotting
a_vars_long <- data_params |>
  dplyr::select(a_netflix, a_tiktok, a_netflix_z, a_tiktok_z) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "value"
  ) |>
  # add category
  dplyr::mutate(
    condition = case_when(
      grepl("netflix", variable) ~ "Netflix",
      grepl("tiktok", variable) ~ "TikTok"
    ),
    type = if_else(grepl("_z$", variable), "z-score", "raw"),
    var_group = "a"
  )

# format long liking data for plotting
strap_vars_long <- data_params |>
  dplyr::select(strap_netflix_avg, strap_tiktok_avg, strap_netflix_avg_z, strap_tiktok_avg_z) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "value"
  ) |>
  # add category 
  dplyr::mutate(
    condition = case_when(
      grepl("netflix", variable) ~ "Netflix",
      grepl("tiktok", variable) ~ "TikTok"
    ),
    type = if_else(grepl("_z$", variable), "z-score", "raw"),
    var_group = "strap"
  )

wl_vars_long <- data_params |>
  dplyr::select(wl_netflix, wl_tiktok, wl_netflix_z, wl_tiktok_z) |>
  pivot_longer(
    cols = everything(), 
    names_to = "variable",
    values_to = "value"
  ) |>
  # add category
  dplyr::mutate(
    condition = case_when(
      grepl("netflix", variable) ~ "Netflix",
      grepl("tiktok", variable) ~ "TikTok"
      ),
    type = if_else(grepl("_z$", variable), "z-score", "raw"),
    var_group = "wl_diff"
  )

# combined long dataset
all_vars_long <- bind_rows(a_vars_long, strap_vars_long, wl_vars_long)

# descriptive statistics table
descriptive_stats <- all_vars_long |>
  dplyr::group_by(var_group, type, condition) |>
  dplyr::summarize(
    n = sum(!is.na(value)),
    mean = mean(value, na.rm = TRUE),
    median = median(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    min = min(value, na.rm = TRUE),
    max = max(value, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::arrange(var_group, type, condition)

# print descriptive statistics
print(descriptive_stats)
```

Visualise the distribution of the estimates, both raw and z-transformed.

```{r}
#| label: visualise descriptives
#| fig-label: descriptive statistics

# densities of wanting variables
a_density_plot <- all_vars_long |>
  dplyr::filter(var_group == "a") |>
  ggplot(aes(x = value, fill = condition)) +
  geom_density(alpha = 0.7, outline.type = "lower", colour = NA) +
  facet_wrap(~type, scales = "free_x", ncol = 1) +
  scale_fill_manual(values = condition_colors) +
  labs(
    title = "Density of 'wanting'",
    subtitle = "Raw values and z-transformed values",
    x = "Value", 
    y = "Density",
    fill = "Condition"
  ) +
  theme_custom() +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "bottom",
    plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 11, hjust = 0.5)
  )

# densities of liking variables
strap_density_plot <- all_vars_long |>
  dplyr::filter(var_group == "strap") |>
  ggplot(aes(x = value, fill = condition)) +
  geom_density(alpha = 0.7, outline.type = "lower", colour = NA) + 
  facet_wrap(~type, scales = "free_x", ncol = 1) +
  scale_fill_manual(values = condition_colors) +
  labs(
    title = "Density of 'liking'",
    subtitle = "Raw values and z-transformed values",
    x = "Value", 
    y = "Density",
    fill = "Condition"
  ) +
  theme_custom() +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "bottom",
    plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 11, hjust = 0.5)
  )

# densities of wanting-liking differences
wl_density_plot <- all_vars_long |>
  dplyr::filter(var_group == "wl_diff") |>
  ggplot(aes(x = value, fill = condition)) +
  geom_density(alpha = 0.7, outline.type = "lower", colour = NA) + 
  facet_wrap(~type, scales = "free_x", ncol = 1) +
  scale_fill_manual(values = condition_colors) +
  labs(
    title = "Density of 'wanting-liking dissociation'",
    subtitle = "Raw values and z-transformed values",
    x = "Value", 
    y = "Density",
    fill = "Condition"
  ) +
  theme_custom() +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "bottom",
    plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 11, hjust = 0.5)
  )

# combine plots
all_density_plot <- all_vars_long |>
  dplyr::mutate(var_group = factor(var_group, levels = c("a", "strap", "wl_diff"), 
                           labels = c("Wanting", "Liking", "Wanting-liking dissociation"))) |>
  ggplot(aes(x = value, fill = condition)) +
  geom_density(alpha = 0.7, outline.type = "lower", colour = NA) +
  facet_grid(type ~ var_group, scales = "free") +
  scale_fill_manual(values = condition_colors) +
  labs(
    title = "",
    subtitle = "",
    x = "", 
    y = "Density",
    fill = "Condition"
  ) +
  theme_custom() +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "bottom",
    plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 11, hjust = 0.5)
  )

# output combined plots overview
all_density_plot
```

## Prior Sensitivity Checks

### Determine sensible priors

```{r}
#| label: compute-default-cauchy

val <- pcauchy(abs(.5), 0, 1/3)
```

Whereas the used scale of 1/3 assigns a prior probability of `r paste0(sprintf("%.3f", val),"%")` to values more extreme than 0.5, the following steps will examine the effect of different prior distributions on our conclusions. To this end, I will compare the group means with a range of different prior settings.

```{r}
#| label: cauchy-distributions

# function: find scale parameter where x% of the distribution are more extreme than effect size threshold y
find_cauchy_scale <- function(x_percent, y_effect, location = 0) {
  
  # convert percent to probability
  x_prob <- x_percent / 100
  
  # function: compute probability assigned to values more extreme than threshold y
  get_prob <- function(scale) {
    # symmetric distribution requires multiplication by two
    2 * (1 - pcauchy(abs(y_effect), location, scale))
  }
  
  # function: find scale where probability of extreme values equals the target proportion x
  objective <- function(scale) {
    (get_prob(scale) - x_prob)^2
  }
  
  # use optim to find minimum
  result <- stats::optimize(objective, interval = c(0.0001, 10))
  
  return(result$minimum)
}

# function: compute scale parameters for combinations of values
create_scale_table <- function(x_percents = c(5, 10, 20, 30, 50), y_effects = c(0.2, 0.5, 0.8), location = 0) {
  
  # create empty matrix for storage
  result_matrix <- matrix(NA, nrow = length(x_percents), ncol = length(y_effects))
  rownames(result_matrix) <- paste0(x_percents, "%")
  colnames(result_matrix) <- paste0("Cohen's d >", y_effects)
  
  # populate matrix
  for (i in 1:length(x_percents)) {
    for (j in 1:length(y_effects)) {
      result_matrix[i, j] <- round(
        find_cauchy_scale(x_percents[i], y_effects[j], location), 3
      )
    }
  }
  
  return(as.data.frame(result_matrix))
}

# compute scale values for the combination between various percentages of more extreme values for different effect sizes
scale_table <- create_scale_table(x_percents = c(5, 10, 20, 30, 50), y_effects = c(0.2, 0.5, 0.8), location = 0)

print(scale_table)
```

The above table illustrates the different scale values of the Cauchy distribution that yield a given percent of effects larger than a small, medium, or large effect. A more conservative approach involves selecting a distribution that is more narrow and assigns less prior probability to effects that are large.

```{r}
#| label: visualise-cauchy
#| fig-cap: "Cauchy distribution for different scale values"
#| fig-align: center
#| out-width: "90%"

# function: plot cauchy distributions
plot_cauchy <- function(scales, location = 0, x_range = c(-2, 2), highlight_y = NULL) {
  
  # create dataframe
  x <- seq(x_range[1], x_range[2], by = 0.01)
  df <- data.frame(x = x)
  
  # add densities for each scale
  for (i in 1:length(scales)) {
    scale_name <- paste("scale", scales[i], sep = "_")
    df[[scale_name]] <- dcauchy(x, location, scales[i])
  }
  
  # reshape data for plotting
  library(tidyr)
  df_long <- pivot_longer(
    df, 
    cols = -x, 
    names_to = "scale", 
    values_to = "density"
  )
  
  # change names for legend 
  df_long$scale_value <- as.numeric(gsub("scale_", "", df_long$scale))
  df_long$scale_label <- paste("scale =", df_long$scale_value)
  
  # create plot
  p <- ggplot(df_long, aes(x = x, y = density, 
                           color = factor(scale_label, levels = paste("scale =", sort(unique(df_long$scale_value)))))) +
    geom_line(size = 1) +
    scale_color_viridis_d(option = "C", begin = 0, end = 0.9) +
    labs(
      title = "",
      x = "Effect size (d)",
      y = "Density",
      color = ""
    ) +
    theme_bw() +
    theme(
      legend.position = "top",
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 10),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
  
  # add vertical lines 
  if (!is.null(highlight_y)) {
    for (y in highlight_y) {
      p <- p + 
        geom_vline(xintercept = y, linetype = "dashed", color = "darkgray") +
        geom_vline(xintercept = -y, linetype = "dashed", color = "darkgray") +
        annotate("text", x = y + 0.1, y = max(df_long$density) * 0.5, label = paste("y =", y), hjust = 0) +
        annotate("text", x = -y - 0.1, y = max(df_long$density) * 0.5, label = paste("y = -", y), hjust = 1)
    }
  }
  
  # add shaded region
  if (!is.null(highlight_y)) {
    
    # create data for shading
    for (y in highlight_y) {
      # lower extreme
      lower_extreme <- data.frame(
        x = seq(x_range[1], -y, by = 0.01)
      )
      # upper extreme
      upper_extreme <- data.frame(
        x = seq(y, x_range[2], by = 0.01)
      )
      
      # add shading
      p <- p + 
        geom_ribbon(data = lower_extreme, 
                    aes(x = x, ymin = 0, 
                        ymax = dcauchy(x, location, min(scales))),
                    fill = "lightgray", alpha = 0.3, inherit.aes = FALSE) +
        geom_ribbon(data = upper_extreme, 
                    aes(x = x, ymin = 0, 
                        ymax = dcauchy(x, location, min(scales))),
                    fill = "lightgray", alpha = 0.3, inherit.aes = FALSE)
    }
  }
  
  return(p)
}

# create plot
p <- plot_cauchy(
  scales = c(scale_table$`Cohen's d >0.2`[2], 
             scale_table$`Cohen's d >0.2`[3], 
             scale_table$`Cohen's d >0.2`[4], 
             scale_table$`Cohen's d >0.2`[5],
             0.707), # default prior in Bayesfactor ttestBF
  highlight_y = c(0.2)
) + theme_custom()

# output plot
print(p)

ggsave(plot = p, filename = "cauchy_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 8, height = 5, bg = "white")
```

@visualise-cauchy illustrates that with smaller scale parameters, the distributions become more peaked around zero and assign smaller probabilities to extreme values. For example, the Cauchy distribution with the scale parameter set to `r sprintf("%.3f", scale_table[[1]][2])` assigns 10% probability to values larger than 0.2. Let's examine the outcomes of the statistical test performed, when using a range of different scale parameters.

## Sensitivity Analysis 1: Prior distributions

The below performs the sensitivity analyses for the Bayesfactor of the main test of this research: hypothesis 2. I will visualise the effect of different prior specifications on the returned Bayesfactor, and subsequently our interpretation. We will sample from a range of 0.05 to 1.

```{r}
#|label: compute-cauchy

val <- pcauchy(abs(.2), 0, 0.05)
```

This lower limit of 0.05 assigns `r sprintf("%.3f%%", (1 - val) * 100)` prior probability to values more extreme than 0.2.

### Hypothesis 1

```{r}
#|label: sensitivity-analysis-scale-h1

# scale vector for sensitivity analysis
bf_scales <- seq(0.05, 1, 0.01)

# compute bayes factors across scale vector
bf_results <- purrr::map_dfr(bf_scales, function(r) {
  
  bf <- BayesFactor::ttestBF(
    x = data_main$a_tiktok,
    y = data_main$a_netflix,
    paired = TRUE,
    rscale = r,
  )
  
  data.frame(r_scale = r, bf = BayesFactor::extractBF(bf)$bf)
  
})

# evidence categories
evidence_category <- cut(bf_results$bf, 
                        breaks = c(-Inf, 1/100, 1/10, 1/3, 3, 10, 100, Inf),
                        labels = c("Extreme", "Strong", "Moderate", "Inconclusive", 
                                  "Moderate", "Strong", "Extreme"),
                        include.lowest = TRUE)

bf_results <- data.frame(
  r_scale = bf_results$r_scale,
  bayes_factor = bf_results$bf,
  evidence_level = evidence_category
)

summary_bf <- summary(bf_results$bayes_factor)
formatC(summary_bf, format = "f", digits = 3)

p1 <- ggplot2::ggplot(bf_results, aes(x = r_scale, y = bayes_factor, color = evidence_level)) +
  geom_line(color = "gray") +  
  # add points colored by evidence level
  geom_point(aes(color = evidence_level), size = 2.5, alpha = 0.9) +    
  # custom color scale for bidirectional evidence
  scale_color_manual(
  name = "Evidence",
  values = c(
    "Inconclusive" = "grey",
    "Moderate" = viridis_colors[2],
    "Strong" = viridis_colors[3],
    "Extreme" = viridis_colors[4]
  ),
  breaks = c("Extreme", "Strong", "Moderate", "Inconclusive", 
             "Moderate", "Strong", "Extreme")
  ) +
  geom_vline(xintercept = 1/3, linetype="dotted", color = "grey", size= 1) +
  labs(
    x = "Prior scale (r)",
    y = "Bayes Factor (BF10)",
    color = "Bayes\nFactor"  
  ) +
  theme_bw() +
  theme(legend.position = "none") + 
  theme_custom() + 
  scale_x_continuous(limits = c(0, max(bf_scales)), breaks = seq(0, max(bf_scales), length.out = 5))

ggsave(plot = p1, filename = "h1_scale_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 8, height = 5, bg = "white")

print(p1)
```

### Hypothesis 2

```{r}
#|label: sensitivity-analysis-scale-h2

# scale vector for sensitivity analysis
bf_scales <- seq(0.05, 1, 0.01)

# compute bayes factors across scale vector
bf_results <- purrr::map_dfr(bf_scales, function(r) {
  
  bf <- BayesFactor::ttestBF(
    x = data_main$wl_tiktok,
    y = data_main$wl_netflix,
    paired = TRUE,
    rscale = r,
  )
  
  data.frame(r_scale = r, bf = BayesFactor::extractBF(bf)$bf)
  
})

# evidence categories
evidence_category <- cut(bf_results$bf, 
                        breaks = c(-Inf, 1/100, 1/10, 1/3, 3, 10, 100, Inf),
                        labels = c("Extreme", "Strong", "Moderate", "Inconclusive", 
                                  "Moderate", "Strong", "Extreme"),
                        include.lowest = TRUE)

bf_results <- data.frame(
  r_scale = bf_results$r_scale,
  bayes_factor = bf_results$bf,
  evidence_level = evidence_category
)

summary_bf <- summary(bf_results$bayes_factor)
formatC(summary_bf, format = "f", digits = 3)

p2 <- ggplot2::ggplot(bf_results, aes(x = r_scale, y = bayes_factor, color = evidence_level)) +
  geom_line(color = "gray") +  
  # add points colored by evidence level
  geom_point(aes(color = evidence_level), size = 2.5, alpha = 0.9) +    
  # custom color scale for bidirectional evidence
  scale_color_manual(
  name = "Evidence",
  values = c(
    "Inconclusive" = "grey",
    "Moderate" = viridis_colors[2],
    "Strong" = viridis_colors[3],
    "Extreme" = viridis_colors[4]
  ),
  breaks = c("Extreme", "Strong", "Moderate", "Inconclusive", 
             "Moderate", "Strong", "Extreme")
  ) +
  geom_vline(xintercept = 1/3, linetype="dotted", color = "grey", size= 1) +
  labs(
    x = "Prior scale (r)",
    y = "Bayes Factor (BF10)",
    color = "Bayes\nFactor"  
  ) +
  theme_bw() +
  theme(legend.position = "none") + 
  theme_custom() +
  scale_x_continuous(limits = c(0, max(bf_scales)), breaks = seq(0, max(bf_scales), length.out = 5))

ggsave(plot = p2, filename = "h2_scale_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 8, height = 5, bg = "white")

print(p2)
```

The above plot illustrates the returned Bayesfactors across the range of prior specifications. Including extremely conservative prior distributions, the smallest returned Bayesfactor is `r sprintf("%.3f", min(bf_results$bayes_factor))`. **The average returned Bayesfactor across the range of prior scale parameters examined is `r sprintf("%.3f", mean(bf_results$bayes_factor))`**, with a median of `r sprintf("%.3f", median(bf_results$bayes_factor))`. Therefore, there is extreme evidence in favour of the alternative hypothesis, which posits that the *wanting-liking* dissociation is different between the TikTok and Netflix conditions.

### Hypothesis 3

```{r}
#|label: sensitivity-analysis-scale-h3

# scale vector for sensitivity analysis
bf_scales <- seq(0.05, 1, 0.01)

# compute bayes factors across scale vector
bf_results <- purrr::map_dfr(bf_scales, function(r) {
  
  bf <- BayesFactor::correlationBF(
  x = data_main$wl_tiktok,
  y = data_main$bsmas_tiktok_total,
  rscale = r
  )
  
  data.frame(r_scale = r, bf = BayesFactor::extractBF(bf)$bf)
  
})

# evidence categories
evidence_category <- cut(bf_results$bf, 
                        breaks = c(-Inf, 1/100, 1/10, 1/3, 3, 10, 100, Inf),
                        labels = c("Extreme", "Strong", "Moderate", "Inconclusive", 
                                  "Moderate", "Strong", "Extreme"),
                        include.lowest = TRUE)

bf_results <- data.frame(
  r_scale = bf_results$r_scale,
  bayes_factor = bf_results$bf,
  evidence_level = evidence_category
)

summary_bf <- summary(bf_results$bayes_factor)
formatC(summary_bf, format = "f", digits = 3)

p3 <- ggplot2::ggplot(bf_results, aes(x = r_scale, y = bayes_factor, color = evidence_level)) +
  geom_line(color = "gray") +  
  # add points colored by evidence level
  geom_point(aes(color = evidence_level), size = 2.5, alpha = 0.9) +    
  # custom color scale for bidirectional evidence
  scale_color_manual(
  name = "Evidence",
  values = c(
    "Inconclusive" = "grey",
    "Moderate" = viridis_colors[2],
    "Strong" = viridis_colors[3],
    "Extreme" = viridis_colors[4]
  ),
  breaks = c("Extreme", "Strong", "Moderate", "Inconclusive", 
             "Moderate", "Strong", "Extreme"),
  drop = FALSE
  ) +
  geom_vline(xintercept = 1/3, linetype="dotted", color = "grey", size= 1) +
  labs(
    x = "Prior scale (r)",
    y = "Bayes Factor (BF10)",
    color = "Bayes\nFactor"  
  ) +
  theme_bw() +
  theme(legend.position = "none") + 
  theme_custom() + 
  scale_x_continuous(limits = c(0, max(bf_scales)), breaks = seq(0, max(bf_scales), length.out = 5))

# create dummy plot to include legend in merged version
dummy_data <- data.frame(
  x = 1:4,
  y = 1:4,
  Evidence_Level = c("Extreme", "Strong", "Moderate", "Inconclusive")
)

dummy_plot <- ggplot(dummy_data, aes(x = x, y = y, color = Evidence_Level)) +
  geom_point() +
  scale_color_manual(
    name = "Evidence",
    values = c(
      "Inconclusive" = "grey",
      "Moderate" = viridis_colors[2],
      "Strong" = viridis_colors[3],
      "Extreme" = viridis_colors[4]
      ),
    breaks = c("Extreme", "Strong", "Moderate", "Inconclusive"),
    drop = FALSE)  +
  guides(linetype = "none", color = guide_legend(direction = "horizontal", title.position = "left"))
  

# Extract legend from dummy plot (this guarantees all colors)
legend_complete <- get_legend(dummy_plot)

print(p3)

ggsave(plot = p3, filename = "h3_scale_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 8, height = 5, bg = "white")

# merge sensitivity analysis plots
hr_sens <- ggpubr::ggarrange(
  p1 + labs(x = ""), 
  p2 + labs(y = ""), 
  p3 + labs(x = "", y = "") + theme(legend.position = "none"),
  ncol = 3, 
  labels = c("A", "B", "C"),
  common.legend = TRUE,
  legend.grob = legend_complete,
  legend = "bottom"
) +  guides(
    linetype = "none",
    color    = guide_legend(direction = "horizontal", title.position = "left")
  )

ggsave(plot = hr_sens, filename = "analyses_scale_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"),
       dpi = 800, width = 12, height = 4, bg = "white")
```

## Evidence accumulation

```{r}
#| label: evidence-accumulation
#| fig-cap: "Bayes Factor accumulation for Hypotheses"
#| fig-align: center
#| message: false
#| warning: false
#| out-width: "90%"

# define shared constants
common_ylim  <- c(1/100, 125)
common_breaks <- c(1/100, 1/10, 1/3, 1, 3, 10, 100)
common_labels <- c("1/100", "1/10", "1/3", "1", "3", "10", "100")

# shared y scaling
shared_y_scale <- function() {
  scale_y_log10(
    breaks = common_breaks,
    labels = common_labels,
    limits = common_ylim,
    expand = expansion(mult = c(0.02, 0.05))
  )
}

# shared colour scale
shared_color_scale <- function() {
  scale_color_manual(
    name = "Evidence",
    values = c(
      "Inconclusive" = "grey",
      "Moderate"     = viridis_colors[4],
      "Strong"       = viridis_colors[3],
      "Extreme"      = viridis_colors[2]
    ),
    breaks = c("Extreme", "Strong", "Moderate", "Inconclusive")
  )
}

## HYPOTHESIS 1
set.seed(123)
data_shuffled <- data_main[sample(nrow(data_main)), ]

bayes_factors <- c()
for (i in 1:(nrow(data_shuffled) - 19)) {
  data_subset  <- data_shuffled[1:(i + 19), ]
  bf           <- BayesFactor::ttestBF(x = data_subset$a_tiktok, y = data_subset$a_netflix, paired = TRUE, rscale = 1/3)
  bayes_factors[i] <- extractBF(bf)$bf
}

evidence_category <- cut(bayes_factors,
  breaks = c(-Inf, 1/100, 1/10, 1/3, 3, 10, 100, Inf),
  labels = c("Extreme", "Strong", "Moderate", "Inconclusive",
             "Moderate", "Strong", "Extreme"),
  include.lowest = TRUE)

n_participants <- 20:nrow(data_shuffled)
plot_data_h1   <- data.frame(n_participants, bayes_factor = bayes_factors, evidence_level = evidence_category)
final_bf_h1    <- sprintf("%.3f", tail(bayes_factors, 1))

p_accum_h1 <- ggplot(plot_data_h1, aes(x = n_participants, y = bayes_factor)) +
  geom_hline(aes(yintercept = 1,     linetype = "Inconclusive"), color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 3,     linetype = "Moderate"),     color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 10,    linetype = "Strong"),       color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 100,   linetype = "Extreme"),      color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/3,   linetype = "Moderate"),     color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/10,  linetype = "Strong"),       color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/100, linetype = "Extreme"),      color = "grey40", size = 0.5) +
  geom_line(color = "grey60", size = 1, alpha = 0.6) +
  geom_point(aes(color = evidence_level), size = 2.5, alpha = 0.9) +
  # top-left anchor: x = -Inf → left edge, y = Inf → top edge
  annotate("text",
           x = -Inf, y = 1/100,
           label    = paste0("Final BF = ", final_bf_h1),
           hjust    = -0.1, vjust = -0.8,
           color    = "black", size = 3.8, fontface = "italic") +
  shared_y_scale() +
  shared_color_scale() +
  scale_linetype_manual(
    name   = "Thresholds",
    values = c("Inconclusive" = "dashed", "Moderate" = "dashed",
               "Strong"       = "dashed", "Extreme"  = "dashed"),
    breaks = c("Inconclusive", "Moderate", "Strong", "Extreme")) +
  theme_bw() + theme_custom() +
    guides(
    linetype = "none",
    color    = guide_legend(direction = "horizontal", title.position = "left")
  ) +
  labs(x = "Participants", y = "Bayes Factor (BF10)", title = "", subtitle = "")

## HYPOTHESIS 2
set.seed(123)
data_shuffled <- data_main[sample(nrow(data_main)), ]

bayes_factors <- c()
for (i in 1:(nrow(data_shuffled) - 19)) {
  data_subset  <- data_shuffled[1:(i + 19), ]
  bf           <- BayesFactor::ttestBF(x = data_subset$wl_tiktok, y = data_subset$wl_netflix, paired = TRUE, rscale = 1/3)
  bayes_factors[i] <- extractBF(bf)$bf
}

evidence_category <- cut(bayes_factors,
  breaks = c(-Inf, 1/100, 1/10, 1/3, 3, 10, 100, Inf),
  labels = c("Extreme", "Strong", "Moderate", "Inconclusive",
             "Moderate", "Strong", "Extreme"),
  include.lowest = TRUE)

n_participants <- 20:nrow(data_shuffled)
plot_data_h2   <- data.frame(n_participants, bayes_factor = bayes_factors, evidence_level = evidence_category)
final_bf_h2    <- sprintf("%.3f", tail(bayes_factors, 1))

p_accum_h2 <- ggplot(plot_data_h2, aes(x = n_participants, y = bayes_factor)) +
  geom_hline(aes(yintercept = 1,     linetype = "Inconclusive"), color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 3,     linetype = "Moderate"),     color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 10,    linetype = "Strong"),       color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 100,   linetype = "Extreme"),      color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/3,   linetype = "Moderate"),     color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/10,  linetype = "Strong"),       color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/100, linetype = "Extreme"),      color = "grey40", size = 0.5) +
  geom_line(color = "grey60", size = 1, alpha = 0.6) +
  geom_point(aes(color = evidence_level), size = 2.5, alpha = 0.9) +
 annotate("text",
           x = -Inf, y = 1/100,
           label    = paste0("Final BF = ", final_bf_h2),
           hjust    = -0.1, vjust = -0.8,       
           color    = "black", size = 3.8, fontface = "italic") + 
  shared_y_scale() +
  shared_color_scale() +
  scale_linetype_manual(
    name   = "Thresholds",
    values = c("Inconclusive" = "dashed", "Moderate" = "dashed",
               "Strong"       = "dashed", "Extreme"  = "dashed"),
    breaks = c("Inconclusive", "Moderate", "Strong", "Extreme")) +
  theme_bw() + theme_custom() +
    guides(
    linetype = "none",
    color    = guide_legend(direction = "horizontal", title.position = "left")
  ) +
  labs(x = "Participants", y = "Bayes Factor (BF10)", title = "", subtitle = "")

## HYPOTHESIS 3
set.seed(123)
data_shuffled <- data_main[sample(nrow(data_main)), ]

bayes_factors <- c()
for (i in 1:(nrow(data_shuffled) - 19)) {
  data_subset  <- data_shuffled[1:(i + 19), ]
  bf           <- BayesFactor::correlationBF(x = data_subset$wl_tiktok, y = data_subset$bsmas_tiktok_total, rscale = 1/3)
  bayes_factors[i] <- extractBF(bf)$bf
}

evidence_category <- cut(bayes_factors,
  breaks = c(-Inf, 1/100, 1/10, 1/3, 3, 10, 100, Inf),
  labels = c("Extreme", "Strong", "Moderate", "Inconclusive",
             "Moderate", "Strong", "Extreme"),
  include.lowest = TRUE)

n_participants <- 20:nrow(data_shuffled)
plot_data_h3   <- data.frame(n_participants, bayes_factor = bayes_factors, evidence_level = evidence_category)
final_bf_h3    <- sprintf("%.3f", tail(bayes_factors, 1))

p_accum_h3 <- ggplot(plot_data_h3, aes(x = n_participants, y = bayes_factor)) +
  geom_hline(aes(yintercept = 1,     linetype = "Inconclusive"), color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 3,     linetype = "Moderate"),     color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 10,    linetype = "Strong"),       color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 100,   linetype = "Extreme"),      color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/3,   linetype = "Moderate"),     color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/10,  linetype = "Strong"),       color = "grey40", size = 0.5) +
  geom_hline(aes(yintercept = 1/100, linetype = "Extreme"),      color = "grey40", size = 0.5) +
  geom_line(color = "grey60", size = 1, alpha = 0.6) +
  geom_point(aes(color = evidence_level), size = 2.5, alpha = 0.9) +
  annotate("text",
           x = -Inf, y = 1/100,
           label    = paste0("Final BF = ", final_bf_h3),
           hjust    = -0.1, vjust = -0.8,        
           color    = "black", size = 3.8, fontface = "italic") + 
  shared_y_scale() +
  shared_color_scale() +
  scale_linetype_manual(
    name   = "Thresholds",
    values = c("Inconclusive" = "dashed", "Moderate" = "dashed",
               "Strong"       = "dashed", "Extreme"  = "dashed"),
    breaks = c("Inconclusive", "Moderate", "Strong", "Extreme")) +
  theme_bw() + theme_custom() +
    guides(
    linetype = "none",
    color    = guide_legend(direction = "horizontal", title.position = "left")
  ) +
  labs(x = "Participants", y = "Bayes Factor (BF10)", title = "", subtitle = "")

# COMBINED FIGURE
accum_legend <- get_legend(p_accum_h2)

accum_all <- ggpubr::ggarrange(
  p_accum_h1 + labs(x = ""),
  p_accum_h2 + labs(y = ""),
  p_accum_h3 + labs(y = "", x = ""),
  ncol = 3, labels = c("A", "B", "C"),
  common.legend = TRUE, legend.grob = accum_legend, legend = "bottom"
)

print(accum_all)

ggsave(plot = accum_all, filename = "evidence_accumulation.png", device = "png",
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"),
       dpi = 600, width = 12, height = 5, bg = "white")
```

## Sensitivity Analysis 3: Exclusion criteria

We preregistered several criteria based on which to exclude participants. These criteria were designed to detect participants who 1) failed to comply to the experimental procedures in meaningful ways that could affect the validity of our manipulation or other aspects of the design, or 2) were inattentive. Participants whose responses suggested they may not have complied with aspects of the design were given the opportunity to provide more detail. In the main manuscript, we considered these text responses in our decision of who to exclude from the analyses in order to ensure that we did not systematically exclude participants who may have been much more strict with themselves (i.e., threshold at which they report having switched a finger being they switched the finger once or twice) or misunderstood the question.

In the below, we report the main results for the different data subsets:

(1) Full dataset: includes all participants for which we have data from both sessions.
(2) Main dataset: includes the dataset used for the analyses in the main manuscript.
(3) Strict dataset: excludes all participants who indicated they had not complied to parts of the experiment, or who failed the preregistered attention check criteria (i.e., both hard or single simple catch question failed).

```{r}
#| label: dataset-versions-s2

# full dataset
dat_full <- data_params

# main dataset
dat_main <- data_params |>
  dplyr::filter(watch_tiktok_compliance == TRUE) |> # exclude TikTok non-compliers
  dplyr::filter(subj_id != p_excl) # exclude Netflix non-compliers
  
# strict dataset
dat_strict <- data_params |>
  dplyr::filter(watch_tiktok_compliance == TRUE) |>
  dplyr::filter(watch_netflix_compliance == TRUE) |>
  dplyr::filter(task_tiktok_compliance == TRUE) |>
  dplyr::filter(task_netflix_compliance == TRUE)
```

After creating the relevant data subsets, let's perform the Bayesian analyses for Hypothesis 1, 2, and 3.

```{r}
#| label: data-sens-h1
#| fig-cap: "Bayes Factors for Hypothesis 1 across different data subsets"
#| fig-align: center
#| message: false
#| warning: false


# dataset list
datasets <- list(
  "dat_full" = dat_full,
  "dat_main" = dat_main, 
  "dat_strict" = dat_strict
)

# compute bayes factors across datasets
bf_results <- purrr::map_dfr(datasets, function(dat) {
  
  bf <- BayesFactor::ttestBF(
    x = dat$a_tiktok,
    y = dat$a_netflix,
    paired = TRUE,
    rscale = 1/3
  )
  
  data.frame(bf = BayesFactor::extractBF(bf)$bf,
             err = BayesFactor::extractBF(bf)$error
             )
  
}, .id = "dataset")

h1_data_sens <- bf_results |>
  ggplot(aes(x = dataset, y = bf, fill = dataset)) +
  geom_col(alpha = 0.8, color = "grey", width = 0.5) +
  labs(
    x = "Dataset",
    y = "Bayes Factor (BF10)"
  ) +
  theme_bw() +
  scale_fill_viridis_d(option = "B", begin = .3, end = .7) +
  theme_custom() +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c(
    "dat_full"   = "Full",
    "dat_main"   = "Main",
    "dat_strict" = "Strict"
  ))

ggsave(plot = h1_data_sens, filename = "h1_data_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 3, height = 4, bg = "white")
```

The above results suggest that our conclusions are not sensitive to the exclusion decisions. Across all three subsets, the data are more probable under the null hypothesis.

```{r}
#| label: data-sens-h2

# compute bayes factors across datasets
bf_results <- purrr::map_dfr(datasets, function(dat) {
  
  bf <- BayesFactor::ttestBF(
    x = dat$wl_tiktok,
    y = dat$wl_netflix,
    paired = TRUE,
    rscale = 1/3
  )
  
  data.frame(bf = BayesFactor::extractBF(bf)$bf,
             err = BayesFactor::extractBF(bf)$error
             )
  
}, .id = "dataset")

h2_data_sens <- bf_results |>
  ggplot(aes(x = dataset, y = bf, fill = dataset)) +
  geom_col(alpha = 0.8, color = "grey", width = 0.5) +
  labs(
    x = "Dataset",
    y = "Bayes Factor (BF10)"
  ) +
  theme_bw() +
  scale_fill_viridis_d(option = "B", begin = .3, end = .7) +
  theme_custom() +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c(
    "dat_full"   = "Full",
    "dat_main"   = "Main",
    "dat_strict" = "Strict"
  ))

ggsave(plot = h2_data_sens, filename = "h2_data_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 3, height = 4, bg = "white")
```

The above suggests that the interpretation of our results is not sensitive to the exclusion criteria, and that across subsets, we find the data to be much more likely under the alternative hypothesis. The data subset reported in the main paper results in the lowest Bayes Factor when comparing the different subsets.

```{r}
#| label: data-sens-h3

# compute bayes factors across datasets
bf_results <- purrr::map_dfr(datasets, function(dat) {
  
  bf <- BayesFactor::correlationBF(
    x = dat$wl_tiktok,
    y = dat$bsmas_tiktok_total,
    rscale = 1/3
  )
  
  data.frame(bf = BayesFactor::extractBF(bf)$bf,
             err = BayesFactor::extractBF(bf)$error
             )
  
}, .id = "dataset")

h3_data_sens <- bf_results |>
  ggplot(aes(x = dataset, y = bf, fill = dataset)) +
  geom_col(alpha = 0.8, color = "grey", width = 0.5) +
  labs(
    x = "Dataset",
    y = "Bayes Factor (BF10)"
  ) +
  theme_bw() +
  scale_fill_viridis_d(option = "B", begin = .3, end = .7) +
  theme_custom() +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c(
    "dat_full"   = "Full",
    "dat_main"   = "Main",
    "dat_strict" = "Strict"
  ))

ggsave(plot = h3_data_sens, filename = "h2_data_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 3, height = 4, bg = "white")

# merge plots

# create merged plot
p_data_sens <- ggpubr::ggarrange(
  h1_data_sens + labs(x = ""),
  h2_data_sens + labs(y = ""),
  h3_data_sens + labs(x = "", y = ""),
  ncol = 3,
  labels = c("A", "B", "C")
)

print(p_data_sens)

ggsave(plot = p_data_sens, filename = "data_sensitivity.png", device = "png", 
       path = here::here("output", "figures", "experiment1", "analyses_sensitivity"), 
       dpi = 800, width = 8, height = 4, bg = "white")
```

Across the different hypotheses we observe a trend of a larger Bayes Factor for the strict subset. In general, the differences between the different subsets make little difference for the overall conclusions.

```{r}
# collect BF results for inline reporting
bf_h1 <- purrr::map_dfr(datasets, function(dat) {
  bf <- BayesFactor::ttestBF(x = dat$a_tiktok, y = dat$a_netflix, paired = TRUE, rscale = 1/3)
  data.frame(bf = round(BayesFactor::extractBF(bf)$bf, 3))
}, .id = "dataset")

bf_h2 <- purrr::map_dfr(datasets, function(dat) {
  bf <- BayesFactor::ttestBF(x = dat$wl_tiktok, y = dat$wl_netflix, paired = TRUE, rscale = 1/3)
  data.frame(bf = round(BayesFactor::extractBF(bf)$bf, 3))
}, .id = "dataset")

bf_h3 <- purrr::map_dfr(datasets, function(dat) {
  bf <- BayesFactor::correlationBF(x = dat$wl_tiktok, y = dat$bsmas_tiktok_total, rscale = 1/3)
  data.frame(bf = round(BayesFactor::extractBF(bf)$bf, 3))
}, .id = "dataset")
```

For **H1**, the Bayes Factors were:
Full = `r sprintf("%.3f", bf_h1 |> filter(dataset=="dat_full") |> pull(bf))`,
Main = `r sprintf("%.3f", bf_h1 |> filter(dataset=="dat_main") |> pull(bf))`,
Strict = `r sprintf("%.3f", bf_h1 |> filter(dataset=="dat_strict") |> pull(bf))`.

For **H2**:
Full = `r sprintf("%.3f", bf_h2 |> filter(dataset=="dat_full") |> pull(bf))`,
Main = `r sprintf("%.3f", bf_h2 |> filter(dataset=="dat_main") |> pull(bf))`,
Strict = `r sprintf("%.3f", bf_h2 |> filter(dataset=="dat_strict") |> pull(bf))`.

For **H3**:
Full = `r sprintf("%.3f", bf_h3 |> filter(dataset=="dat_full") |> pull(bf))`,
Main = `r sprintf("%.3f", bf_h3 |> filter(dataset=="dat_main") |> pull(bf))`,
Strict = `r sprintf("%.3f", bf_h3 |> filter(dataset=="dat_strict") |> pull(bf))`.